
\newcommand{\bloodpowers}{Blood Powers}
\newcommand{\bloodpowersInitial}{BP}

\newcommand{\bloodpowersintroduction}{%
	Vampire Counts and Vampire Courtiers \textbf{must} purchase unique upgrades called Blood Powers. These powers can be duplicated within the army unless specifically stated otherwise. A model may only have a single Ancestral Blood Power.
}

\newcommand{\ancestralbloodpowers}{Ancestral Blood Powers}
\newcommand{\greaterbloodpowers}{Greater Blood Powers}
\newcommand{\lesserbloodpowers}{Lesser Blood Powers}
%% Names

\newcommand{\brotherhoodofthedragon}{Brotherhood of the Dragon}
\newcommand{\vonkarnstein}{Von Karnstein}
\newcommand{\lahmia}{Lahmia}
\newcommand{\strigoi}{Strigoi}
\newcommand{\nosferatu}{Nosferatu}

\newcommand{\crimsonrage}{Crimson Rage}
\newcommand{\stormcaller}{Storm Caller}
\newcommand{\commandment}{Commandment}
\newcommand{\ghoullord}{Ghoul Lord}
\newcommand{\arcaneknowledge}{Arcane Knowledge}

\newcommand{\supremelich}{Supreme Lich}
\newcommand{\eternalduellist}{Eternal Duellist}
\newcommand{\monsterhunter}{Monster Hunter}
\newcommand{\unbreakablewill}{Unbreakable Will}
\newcommand{\mesmerisinggaze}{Mesmerising Gaze}
\newcommand{\bestialbulk}{Bestial Bulk}
\newcommand{\flyinghorror}{Flying Horror}
\newcommand{\mysteriesofthenight}{Mysteries of the Night}

%% Dominant Powers

\newcommand{\brotherhoodofthedragonrestriction}{Cannot be taken by Wizard Masters}
\newcommand{\brotherhoodofthedragondef}{
	 The model part gains Plate Armour, \textbf{Weapon Master}, and can take any number of Close Combat Weapons.
}

\newcommand{\vonkarnsteindef}{
	  The model gains \textbf{Awaken (\batswarms, \direwolves, \greatbats, \zombies)}, \textbf{\commandingpresence{}  (\distance{+6})}, and \textbf{\rallyaroundtheflag{}  (\distance{+6})}. In addition, the model's unit gains \textbf{Autonomous}.
	 \columnbreak
}

\newcommand{\lahmiarestriction}{Cannot be taken by models with Heavy Armour and/or Shield}
\newcommand{\lahmiadef}{
	 The model part gains \textbf{Distracting} and \textbf{Lightning Reflexes}.
}

\newcommand{\strigoirestriction}{Models on foot or mounted on Shrieking Horror only. Cannot be taken by models with any Armour Equipment and/or Wizard Masters}
\newcommand{\strigoidef}{
	The model part's Health Points are \textbf{set} to 4, and it gains \textbf{Fortitude (4+)} and \textbf{Hatred}.
}

\newcommand{\nosferaturestriction}{Wizards only. Cannot be taken by models with Heavy Armour and/or Shield}
\newcommand{\nosferatudef}{
	 The model gains \textbf{Gates of the Netherworld} and \textbf{Awaken (Skeletons, Zombies)}, and it knows the Hereditary Spell in addition to its other spells.
}

%% Vampire Count Powers

\newcommand{\crimsonragerestriction}{Vampire Counts with Brotherhood of the Dragon only}
\newcommand{\crimsonragedef}{
	 The model part gains \textbf{Battle Focus} and \textbf{must} reroll failed to-hit rolls.
}

\newcommand{\stormcallerrestriction}{Vampire Counts with Von Karnstein only}
\newcommand{\stormcallerdef}{
	All units within \distance{12} of the model gain \textbf{Hard Target (1)}.
}

\newcommand{\commandmentrestriction}{Vampire Counts with Lahmia only}
\newcommand{\commandmentdef}{
	The Defensive Skill and Offensive Skill of \rnf{} models in the model's unit are \textbf{set} to 6.
}

\newcommand{\ghoullordrestriction}{Vampire Counts with Strigoi only}
\newcommand{\ghoullorddef}{
	The model and all \rnf{} models in its unit gain \textbf{Poison Attacks}. If the \rnf{} models already had Poison Attacks, they wound automatically on a successful natural to-hit roll of \result{5} or \result{6}, unless the target has \immune{} (\poisonattacks{}).
}

\newcommand{\arcaneknowledgerestriction}{Vampire Counts with Nosferatu only}
\newcommand{\arcaneknowledgedef}{
	Spells cast by the model gain +\distance{6} range. Aura spells gain +\distance{3} range instead. Bound Spells and spells without range are not affected.
}

%% Other Powers

\newcommand{\supremelichrestriction}{ Vampire Courtiers with Nosferatu only}
\newcommand{\supremelichdef}{The model becomes a Wizard Master.}

\newcommand{\eternalduellistdef}{%
	The model part \textbf{must} reroll natural to-hit and to-wound rolls of \result{1} with its Close Combat Attacks.%
}

\newcommand{\monsterhunterdef}{%
	The model part gains \textbf{Multiple Wounds (2, against Towering Presence)}.%
}

\newcommand{\mesmerisinggazedef}{%
	 Whenever possible, unless another model does so first, the model \textbf{must} accept or issue a Duel. Duels issued by the model \textbf{must} (if possible) be accepted by a Character unless a Champion accepts first. Enemy model parts without Harnessed fighting a Duel with the model suffer −1 Attack Value.%
}

\newcommand{\bestialbulkrestriction}{ Models on foot only}
\newcommand{\bestialbulkdef}{%
	The model's Height is changed to Large and its base size to 40\timess{}\SI{40}{\milli\meter}. While joined to a unit of Ghasts, the model gains Scoring. If playing Capture the Flags, the model gains Scoring (no matter if joined to a unit of Ghasts or not).
}

\newcommand{\unbreakablewilldef}{%
	At the start of each Round of Combat, select a single friendly unit Engaged in the same Combat as the model (this can be the models's own unit). This unit gains \textbf{\stubborn} until the end of the Melee Phase.%
}

\newcommand{\flyinghorrordef}{%
	The model gains \textbf{\fly{7}{14}}, \textbf{\lighttroops}, and \textbf{\swiftstride}.%
}

\newcommand{\mysteriesofthenightrestriction}{ Wizard Apprentices and Adepts only}
\newcommand{\mysteriesofthenightdef}{
	 The model's Path Access is replaced with Cosmology, Shamanism, and Witchcraft.
}
