
\newcommand{\vampiricbloodlines}{Vampiric Bloodlines}
\newcommand{\vampiricbloodlinesInitial}{VB}

\newcommand{\vampiricbloodlinesintroduction}{%
	The Vampire Covenant army may choose to represent a single Vampiric Bloodline. In this case, all Vampire Counts and Vampire Courtiers in such a Bloodline Army \textbf{must} take the upgrade that corresponds to that Bloodline. All rules associated with a Vampire are only applied to the model part that takes the upgrade and do not apply to any mounts unless specifically stated otherwise.%
}

\newcommand{\ancientbloodpower}{Ancient Blood Power}
\newcommand{\ancientbloodpowerdef}{%
	Bloodline Vampire Counts can take the Ancient Blood Power of their Bloodline instead of taking a Blood Power. All Ancient Blood Powers are \zerotoXperarmy{1}.%
}

\newcommand{\bloodties}{Blood Ties}
\newcommand{\bloodtiesdef}{%
	Certain unit entries in this Army Book include the term Blood Ties, followed by the name of a Bloodline in brackets. If the army includes at least one Vampire Count or Vampire Courtier matching the Bloodline written in brackets in a unit entry, this unit gains access to the associated Blood Ties option.
}

\newcommand{\pathaccess}{The Vampire's Path access is replaced with}


\newcommand{\brotherhoodofthedragonbloodline}{Brotherhood of the Dragon Bloodline}
\newcommand{\brotherhoodofthedragonbloodlinedef}{%
	The Vampire gains +2 Offensive Skill, \textbf{\pa}, \textbf{\weaponmaster}, and can take any number
of Close Combat Weapons. Whenever possible, unless another model does so first:%
	\begin{itemize}%
		\item The Vampire \textbf{must} accept a Duel.
		\item The Vampire \textbf{must} issue a Duel.
	\end{itemize}%
	Vampire Courtiers cannot be upgraded to Wizard Adepts. Vampire Counts cannot be upgraded to Wizard Masters.%
}



\newcommand{\vonkarnsteinbloodline}{Von Karnstein Bloodline}
\newcommand{\vonkarnsteinbloodlinedef}{%
	The Vampire \textbf{must} reroll failed Vampiric rolls, and the presence of one or more Von Karnstein Vampires grants +1 to their side's Combat Score in any combat which they are Engaged in. Models in the same unit as a Von Karnstein Vampire gain \textbf{\autonomous{}}. If applicable, the ranges of Commanding Presence and Rally Around the Flag of Von Karnstein Vampires are increased by \distance{6}.%
}

\newcommand{\lamia}{Lamia}
\newcommand{\lamiabloodline}{Lamia Bloodline}
\newcommand{\lamiabloodlinedef}{%
	The Vampire gains \textbf{\lightningreflexes{}} and suffers \minuss{}1 Attack Value. Enemy units in base contact with one or more Lamia Vampires suffer \minuss{}1 Agility. If the Vampire is not equipped with \ha{} and/or a \shield{}, it gains \textbf{\distracting{}}. Duels issued by the Vampire \textbf{must} (if possible) be accepted by a Character unless a Champion accepts first. Enemy model parts without Harnessed in a Duel with the Vampire suffer \minuss{}1 Attack Value.%
}


\newcommand{\strigoibloodline}{Strigoi Bloodline}
\newcommand{\strigoibloodlinedef}{%
	The Vampire gains \textbf{\fortitude{} (4+)}, \textbf{\hatred{}}, and +1 Health Point, cannot take a mount except
for a \shriekinghorror{}, and may not be equipped with any kind of armour. Vampire Courtiers cannot be upgraded to Wizard Adepts. Vampire Counts cannot be upgraded to Wizard Masters.%
}

\newcommand{\nosferatubloodline}{Nosferatu Bloodline}
\newcommand{\nosferatubloodlinedef}{%
	The Vampire suffers \minuss{}1 Attack Value, \minuss{}2 Offensive Skill, and may not be equipped with \ha{} and/or a \shield{}. The Vampire gains \textbf{\awaken{} (\skeletons{}, \zombies{})} and \textbf{\gatesofthenetherworld{}}. A Vampire Courtier \textbf{must} be upgraded to Wizard Apprentice, Wizard Adept, or Wizard Master. A Vampire Count \textbf{must} be upgraded to Wizard Adept or Wizard Master. The Vampire always knows the Hereditary Spell in addition to its other spells.%
}
