
\newcommand{\fluffone}{%
	Sagas and runestones are the most important forms of literature among the \AA{}sklanders, for they are the source of tradition, the whole of their myth, ethics, and political art. In such poems we can find evidence of the shifting religious tradition and the progressive takeover of temples and tribes by gods coming from the Wasteland. Such \enquote{contamination} has not changed the true nature of the \AA{}sklanders, which is still connected at its roots to the ancient culture they share with Sonnstahl. Far from being a nation, the land is a patchwork of tribes, each with its own agenda. Some are friendly to our Empire, such as the Kingdom of Thrymland, others hostile, often changing according to the relationships forged between their kings and jarls and our own nobility. The fragments we hereby present were selected to provide a complete and characterful description of the very essence of \AA{}skland and its people, to paint a picture of the manifold cultures and creatures among our northern \enquote{cousins}.\fluffref{Grünberg Brothers, introduction to the collection of the Literature of the Thrymland}%
}

\newcommand{\flufftwo}{%
	\AA{}sklanders are fierce fighters; that reputation has spread far and wide. I've fought against them for decades, and the descriptions of berserkers and wild warriors are well earned. Yet in all those warning tales, there is an aspect which is often overlooked.
	
	They know well how to fight in great numbers, and somehow they manage not to get in each other's way. Each leaps forward to strike terrible blows with huge axes, only to be replaced by another, and another. No elven formation of grace and discipline, but effective nonetheless.
	
	In defence they are even more concerted. Those round, studded shields interlock to form a solid wall against which enemies crash in waves. I've seen many an elite soldier underestimate \AA{}sklanders as mere savages---only to suffer for their folly.\fluffref{Shepkin Tikhonovich---Volskayan Voivoda}%
}

\newcommand{\fluffthree}{%
	So I am to be married. I feel equal parts dread and joy---and as usual I have been burying these emotions in reading. My husband is to be Prince Olvir Hrogtharson, son of the King of Thrymland, the famous Hrogthar Alfhildr. I am to share my bed with an \AA{}sklander! I have consumed every book on the subject of that wild land---the stories have only worsened the fragile state of my imagination. \AA{}skland is a patchwork of tribes divided up by Kings, Jarls, and Hersirs. Many are barbaric and unruly---often meddling in worship of the Dark Gods. \AA{}sklanders are famous for their raiding and trading vessels that can be found in ports as far as Avras and Aldan. For a long time they were Sonnstahl's enemies, but in our time the comparatively civilised nation of Thrymland has been supported by the Emperor as part of a bulwark against the northern tribes. I suppose my status as a pawn in these negotiations should bring me pride. I only hope that I can conquer this awful terror and do my duty to father and nation.\fluffref{Diary of Lady Annelie, daughter of the\\ Count of Breidmark}%
}


\newcommand{\asklanderchieffluff}{%
	To lead is the destiny of the jarls and hersirs. But leading should be tested: trials must be endured and challenges won, for a chieftain should prove not only the strongest of the tribe, but the wisest also. Proud and dauntless, feared and respected, such are the demands of leadership.%
}


\newcommand{\seidhkennarfluff}{%
	Seidhkennars are the voice of the gods, advisers of the jarls, guides to the berserkers. They are tellers of sagas, masters of magic, and speakers with all the creatures of the North. No force would dare to raid without their blessing, nor a king march to war: for the seers of \AA{}skland know the spirit of the land.%
}


\newcommand{\asklandersfluff}{%
	The \AA{}sklander is a fighter to be feared: strengthened by harsh living and long hunts through the forest, each man and maiden of our people is skilled with axe or bow and born to raiding.%
}


\newcommand{\warhoundsfluff}{%
	Hunting is our oldest and most indispensable tradition. The deepest bonds of man and beast are forged from the cradle with our hunting packs. Our hounds are no foppish southern pups, but proud heirs of the great wolves of the northern forest. Long generations of careful stewardship have created one of the smartest and most dangerous breeds of warhounds ever seen.%
}


\newcommand{\flayersfluff}{%
	Riding huge wolves, spiders, and all manner of breakneck beasts, the role of the flayer is reserved for the most courageous and aggressive members of our tribes. Often hardened survivors without families, flayers are among the most feared of those we dread to face. Their speed and brutality is like a vicious blizzard, scouring the flesh and obliterating all hope.%
}


\newcommand{\asklanderhorsemenfluff}{%
	Mounts are considered a privilege among the most important \AA{}sklander families. They are generally given to the youngest warriors, to prove themselves as scouts and vanguards of raiding forces, as there is limited space for horses on a longboat.%
}


\newcommand{\warriorsfluff}{%
	\AA{}sklanders who have sworn to the Dark Gods often return to their homes to fulfil their path, for reasons that are unclear even to seidhkennars. Nonetheless, they are always welcomed among the ranks of a raiding party, as their prowess in battle is doubted by none.%
}


\newcommand{\wargsfluff}{%
	Wargs are not mere pet wolves, trained to attack on command. They are born of Ullr's fury, impervious to the rigours of a mountain winter, tougher and sometimes larger than a horse. A single warg can down a giant elk if it catches it unaware, and a pack is a serious danger even to well-armed travellers. You are never free of the warg's nose. It will track you for days if it deems you a worthy prize. If you are fierce enough, you can steal the pups and harness this fury yourself: but be sure to serve Ullr well, or you'll be a meal for the beast soon enough.%
}


\newcommand{\icetrollsfluff}{%
	Trolls are hardy creatures. So much so, that it is rumoured neither man nor nature can kill them. The beasts that inhabit the frozen lands are no exception. As grotesque, greedy, and ill-tempered as their southern cousins, their tough, icy hide emits a palpable aura of cold so fierce it has even been known to extinguish fire.%
}


\newcommand{\huskarlsfluff}{%
	No one can become a jarl without the support of the huskarls, and new jarls are often elected from their number, for they are not only bodyguards but a warrior elite. Seasoned fighters, their wisdom and ruthlessness in matters of war and raiding is rarely matched by younger warriors and chiefs.%
}


\newcommand{\berserkersfluff}{%
	Gnashing teeth, crazed howling, deranged biting of shields---a ferocious blur of axes, bleeding steel, and bear pelts: these are the berserkers of Vigi. He asked of them to be the nightmare of the elven enemy, and they became as such. They do not fear death, nor defeat, for their only purpose is killing elves.%
}


\newcommand{\krakenfluff}{%
	The most experienced raiding jarls and seidhkennars develop a deep connection with the seas, and have even proved able to tame and master these legendary creatures, often luring them away from isolated forces of dread elves.%
}


\newcommand{\maraudinggiantfluff}{%
	Those few giants living near our settlements are accepted and looked after by most tribes. While they are generally solitary and unpredictable beings, they usually learn how to behave on an expedition, and often develop strong bonds with individual \AA{}sklanders.%
}


\newcommand{\joetunnfluff}{%
	Walk upon a mountainous road, and you may find yourself in the vicinity of one of the mightiest creatures to inhabit the earth---a jötunn.

	The first you will know is the drop in temperature; your skin will burn and your bones freeze, until you can barely crawl. A mist of freezing air will rise around you. The next sign is the ground shuddering; the very mountain appears to split, until blue-grey flesh resolves from blue-grey rock.

	Last, eyes open. Vast eyes, with a red hue, taking moments to focus upon the tiny creatures before it.

	If you are fortunate, you will be accompanied by a seidhkennar, who can fathom the landslide rumbling that passes for language between them. If you are truly blessed, your guide can settle that mountain back to sleep, before the mighty being decides to crush those who disturb its slumber.

	Returning to cold stone's embrace, it might be years before the jötunn rises again, but time seems to matter little to their kind. I simply pray I am never the cause of their ire, or have reason to defend against them---castle walls can only do so much!\fluffref{My Time in the North---Lionel Bethune,\\ Baron of Equitaine}%
}
