\newcommand{\howdahdevices}{Howdah Devices}
\newcommand{\howdahdevicesInitial}{HD}

\newcommand{\howdahspecification}{
	Howdah Devices are upgrades that certain Saurian Ancients models may take. If one model in a unit is upgraded with a Howdah Device, all other models in the unit must be upgraded with the same Howdah Device as well.
}

\newcommand{\engineoftheancients}{Engine of the Ancients (3+)}
\newcommand{\engineoftheancientsrestriction}{\zerotoXmodelsperarmy{3}}
\newcommand{\engineoftheancientsdef}{
	Shooting Weapon. \range{12}, \shots{1}, \St{} 6, \AP{} 3, \textbf{\areaattack{} (2\timess{}2)}, \textbf{\lodestone{}}, \textbf{\marchandshoot{}}, \textbf{\reload{}}. The attack \textbf{never} suffers negative to-hit modifiers. For the purpose of shooting this weapon, the model can draw Line of Sight in any direction, even outside its Front Arc.
}

\newcommand{\venomousfortress}{Venomous Fortress}
\newcommand{\venomousfortressrestriction}{\zerotoonemodelsperarmy{}. Thyroscutus Herd only}
\newcommand{\venomousfortressdef}{
	The model’s base size is changed to 60×100 mm and it gains 6 additional Skink Riders. If applicable, Exclusive (Tegu Warriors, Tegu Guard) is replaced with Exclusive (Skink Warriors, Skink Hunters). In addition, model parts without Harnessed in the bearer’s unit gain \textbf{\hatred} and \textbf{\poisonattacks}.
}

\newcommand{\monolithofvitalism}{Monolith of Vitalism}
\newcommand{\monolithofvitalismrestriction}{One of a Kind}
\newcommand{\monolithofvitalismdef}{
	The model becomes the Battle Standard Bearer.
}

\newcommand{\suncatchercrystal}{Suncatcher Crystal}
\newcommand{\suncatchercrystalrestriction}{\zerotoXmodelsperarmy{3}}
\newcommand{\suncatchercrystaldef}{
The model gains \grindattacks{2\Dthree{}} that are \textbf{always} resolved with Strength 4 and Armour Penetration 1. In addition, when calculating Combat Score, a side with one or more Suncatcher Crystals adds +1 to its Combat Score.
}

\newcommand{\lodestoneshield}{Lodestone Shield}
\newcommand{\lodestoneshieldrestriction}{\zerotoonemodelsperarmy{}}
\newcommand{\lodestoneshielddef}{
	Friendly units within \distance{8} of the model gain \textbf{\aegis{} (5+, against Shooting Attacks)}.	
}

\newcommand{\magneticgreatbow}{Magnetic Great Bow (3+)}
\newcommand{\magneticgreatbowrestriction}{\zerotoXmodelsperarmy{3}}
\newcommand{\magneticgreatbowdef}{
	Shooting Weapon. \range{18}, \shots{2}, \St{} 4 [5], \AP{} 1 [3], \textbf{\areaattack{} (1\timess{}5)}, \textbf{\lodestone{}}, \textbf{\marchandshoot{}}, \textbf{\reload{}}.
}

\newcommand{\carvedwisdom}{Carved Wisdom}
\newcommand{\carvedwisdomrestriction}{\zerotoXmodelsperarmy{3}}
\newcommand{\carvedwisdomdef}{
During Spell Selection, the model \textbf{must} choose one of the spells below. The model can cast the chosen spell as a Bound Spell with Power Level (4/8):
	\begin{itemize}
		\item \spellformat{\divinationspelltwo{}}{\divination}
		\item \spellformat{\druidismspellfour{}}{\druidism}
		\item \spellformat{\alchemyspellsix{}}{\alchemy}
		\item \spellformat{\shamanismspelltwo{}}{\shamanism}
		\item \spellformat{\evocationspellfive}{\evocation}
	\end{itemize}
	Each spell can only be chosen by a single model with \carvedwisdom{}.
	\columnbreak
}