\newcommand{\arcanemasteries}{Arcane Masteries}
\newcommand{\arcanemasteriesmustchooseonlyone}{\textbf{Must} choose a single Arcane Mastery}

\newcommand{\eideticmastery}{Eidetic Mastery}
\newcommand{\telepathicmastery}{Telepathic Mastery}
\newcommand{\conjurationmastery}{}
\newcommand{\mindshiftingmastery}{Mind\minuss{}Shifting Mastery}
\newcommand{\forbiddenmastery}{Forbidden Mastery}
\newcommand{\eternalmastery}{Eternal Mastery}
\newcommand{\veilmastery}{Veil Mastery}


\newcommand{\eideticmasterydef}{
	The model knows  two additional Learned Spells.
}

\newcommand{\telepathicmasterydef}{
	Once per friendly Magic Phase, the model may attempt to cast a single non-Hereditary Learned Spell that was successfully cast by an enemy Wizard during the preceding Magic Phase. If that spell is successfully cast, the model may cast an Attribute Spell that the enemy Wizard knows for the non-Hereditary Learned Spell, if available.
}

\newcommand{\conjurationmasterydef}{}%


\newcommand{\mindshiftingmasterydef}{
\newrule{After successfully casting a Learned Spell, the model may choose the Attribute Spell of Alchemy, Divination, Evocation, or Witchcraft. If the Learned Spell has an Attribute Spell that the owner wishes to cast (even if it is identical to the chosen Attribute Spell), the chosen Attribute Spell may be cast immediately before or after casting the Learned Spell's Attribute Spell. Otherwise, the chosen Attribute Spell is cast immediately after resolving the Learned Spell's effects.}\columnbreak
}

\newcommand{\forbiddenmasterydef}{
	The model knows two additional Learned Spells that it \textbf{must} select from the Learned Spells 1, 2, 3, and 4 from Pyromancy, otherwise following the normal Spell Selection rules. In each Magic Phase, when the model successfully casts a spell from Pyromancy for the first time, the model's unit gains Maximised (Discipline Tests) until the start of the next friendly Magic Phase.	
}

\newcommand{\eternalmasterydef}{
	The model gains a +1 Casting Modifier.
}

\newcommand{\veilmasterydef}{
	The model gains Channel (1). In addition, the owner gains 1 Veil Token every time the model successfully casts a non-Bound and non-Attribute Spell, after resolving the spell’s effect and any Attribute Spell.}