% Special Equipment Names

\newcommand{\wildfireburst}{Wildfire Burst}
\newcommand{\hawthorncurse}{Hawthorne Curse}
\newcommand{\symbolofslaughter}{Symbol of Slaughter}
\newcommand{\wastelandtorch}{Wasteland Torch}
\newcommand{\mammothhidecloak}{Mammoth-Hide Cloak}
\def\endlessplain{Endless Plain}
\newcommand{\spiritoftheherd}{Spirit of the Herd}
\newcommand{\turulradiantheaddress}{Turul Radiant Headdress}

% Special Equipment Texts

\newcommand{\wildfireburstdef}{%
	This weapon has \shots{4}, \St{} 4, \AP{} 1 and \textbf{always} hits on 3+. Attacks made with this weapon gain \textbf{Flaming Attacks} and \textbf{Magical Attacks}. A unit that is hit by these attacks loses Soft Cover until the end of the Player Turn (if it had it). If the enemy unit was in Hard Cover, it is now considered to be in Soft Cover until the end of the Player Turn.%
}
\newcommand{\hawthorncurserestriction}{Models without \ambush{} only}
\newcommand{\hawthorncursedef}{%
	Attacks made with this weapon gain \textbf{\devastatingcharge{+2 \St{}, +2 \AP{}}} and become \textbf{\magicalattacks}. The weapon can be used as a Shooting Weapon (3+) with the following profile: \range{18}, \shots{1}, \St{} 3 [6], \AP{} 10, \textbf{\areaattack{} (1\timess{}5)}, \textbf{\reload}, [\textbf{\multiplewounds{D3}{}}]. This Shooting Attack never suffers negative to-hit modifiers.%
}
\newcommand{\symbolofslaughterdef}{%
	When using this weapon, the wielder gains +2 Attack Value, +2 Agility, and \textbf{\magicalattacks{}}. Close Combat Attacks made against the wielder's model gain +1 to hit.%
}
\newcommand{\wastelandtorchdef}{%
	The bearer's unit gains \textbf{\strider{} (\ruins{})}. After determining Deployment Zones (at the end of step 6 of the Pre-Game Sequence), you may choose a single Field or Forest Terrain Feature that becomes Ruins. The bearer's unit gains \textbf{\flamingattacks{}} in the First Round of Combat.%
}
\newcommand{\mammothhidecloakrestriction}{Standard Height only}
\newcommand{\mammothhidecloakdef}{%
	The wearer gains +1 Armour. Attacks against the wearer can \textbf{never} have a Strength above 5.%
}
\def\endlessplaindef{%
	After determining Deployment Zones (at the end of step 6 of the Pre-Game Sequence), place a single Field Terrain Feature that \textbf{must} be no larger than \distance{10} in length and \distance{6} in width completely outside the opponent's Deployment Zone.%
}
\newcommand{\spiritoftheherddef}{%
	Model parts without Harnessed in the bearer's unit gain \textbf{Devastating Charge (Lightning Reflexes)}.%
}
\newcommand{\turulradiantheaddressrestriction}{Standard Height only} 
\newcommand{\turulradiantheaddressdef}{%
	The bearer gains \textbf{\distracting{}} and \textbf{\terror{}}.%
}	

