
\newcommand{\fluffone}{%
	The Makhar Steppe breeds tough inhabitants. Only through total commitment to our people can we Makhar survive the inhospitable, endless plains and the ravaging creatures therein. Loyalty is expected and demanded of all, weakness cannot be tolerated. Our allies are the beasts of the Steppes; horse, dog, mighty turul, and mammoth, amongst others. Our code is one of war in the face of relentless struggle. From the depths of the mighty Steppe our war hordes strike with elemental force. Our speed and ferocity are legendary. Not for us, the soft and easy life of the settled people to our West. We are the children of the grass, the sky, and the wind, and we bring with us death.

	My trusted kinsman, Munkács, will show you the might of our army; heed his words and mind yours, you are not among friends here. Whilst I will honour the terms of the negotiations and refrain from spilling your blood, my people may not show you such courtesies. Feast your eyes on our might and report back to your masters. Tell them their demise is at hand should they refuse our demands.%
	\fluffref{Gyula Gesimus' greeting to the Empire's diplomats whilst at camp, three days march east of Volskagrad} 
}


\newcommand{\flufftwo}{%
	A swarthy warrior steps forward. His contempt for us is evident from the sneer which he barely attempts to hide. Stopping unpleasantly close to me he leers in the most appalling manner. Cowering behind him is a beaten curr of a man, his garb is reminiscent of that worn in Equitaine, evidently he is a captive of this Munkács. The stench from him is palpable, even from this distance but a glint in his eye indicates that some of the arrogance of his people remains.%

	\enquote{Greetings Munkács, warrior of the Great Gyula.} I release my practiced charm, but it has little effect.%

	\enquote{Follow me, pampered weaklings of the settled lands. Dung Boy, see to his belongings.} Munkács inclines his head towards the wretch and then towards my baggage.%

	\enquote{Yes, master, I shall. Right away\dots{}}%

	With that, the contemptuous warrior spins nimbly on his heel, walking purposefully into the depths of the camp. %

	I follow behind him.%
	\fluffref{Account of Marzell von Stirlingen, Imperial diplomat, recounting the words of Munkács and his band in the Imperial account of the war parties reported to be massing beyond the Beacons.}%
}


\newcommand{\fluffthree}{%
	Dung Boy I may be now, but not always. I used to be a warrior, a Questing Knight no less. Thirty years I served The Lady at war. I've fought them all and journeyed far and wide to do so, smashing through their lines with our lances. None could stand before us. But these Makhar, the only defeat I ever knew. We were on campaign in Northern Taphria when we met the Steppe Horsemen. Our scouts brought tales of their skill in battle and so we took appropriate countermeasures. But their horses never came, just hordes of Tamyir Vassals on foot. Apparently the Makhar scouts had gotten closer than we thought and our ruse was diffused. Their screaming infantry quite spooked the levies and no matter how hard I beat them they ran. Our lines were overrun in a trice. The Duke rallied the Knights and charged, but their warriors just melted away before our lances and as our mounts tired we were hit by all manner of Makhar monstrosities. Heavy cavalry wielding those horrific double handed lances, chariots swarming with Makhar, giants carrying bolt throwers and all the time arrows raining down from the sky like death. Then the mammoths joined the fray and I was, err, knocked unconscious. I came to as a prisoner and the only survivor. It's not much of a life shovelling dung, but it's still a life eh?%

	I say, you don't have any wine do you?%
	\fluffref{Account of Marzell von Stirlingen of his meeting with Baron Luis de Châtray}%
}


\newcommand{\makhargyulafluff}{%
	Our Gyulas lead by example, gifted leaders, as skilled in war as they are in holding together the fractious elements of our people. This is no easy task and many fall to the usurper's blade or the enemy's spear. Those that master this enigmatic art are elevated almost to the status of gods. When their time on the Steppe is at an end we raise massive earth mounds to house their treasures in this realm and the next. The weak are left in the grass for the wolves.%
}


\newcommand{\taltosfluff}{%
	There are some amongst us who see that which is beyond most Makhar. They perceive the living, beating heart of the Steppe, feel the pulsing rhythms of the winds, and commune with the spirit of our land. Their way is no easy path, these Táltos; they are as much part of our war horde as the horses or bows. We expect them to fight alongside us, to live and die as we do, in the cauldron of battle. Their skills which bring the power of the Steppe crashing into our enemies has turned many battles in our favour.%
}


\newcommand{\steppewolfhoundsfluff}{%
	The Steppe harbours many fearsome beasts. As children we learn of these terrors---the stories told around the fire create a healthy fear. The young are entrusted to guard the herds, and to aid them we keep dogs. These are no fireside lapdogs familiar to the settled people, but bred over centuries as the fiercest and fastest of their kind.%
}


\newcommand{\tamyirvassalsfluff}{%
	We were ready for their horsemen, knew they would be coming. Spent all day digging shallow pits and covering them with mown grass to break their horses' legs. Well, the peasants did, obviously I only supervised. But the horses never came, just hordes of wild Tamyir Vassals on foot. We were overrun in a heartbeat.%
	\fluffref{Baron Luis de Châtray, formerly an Equitan Questing Knight, latterly a dung shoveller}%
}


\newcommand{\horsearchersfluff}{%
	Our warrior code is a way of life and it extends to our horses, the closest and oldest of our allies. Their loyalty is complete and ancient, our families and their bloodlines intertwine far beyond the telling. We are as one. We live or die, together. All Makhar can ride and are masters of the bow, our survival demands it and no man can match us. We ride before we walk and shoot before we talk. With our bows a Makhar Horse Archer is to be feared, appearing without warning and fading away as fast. The last sound many have heard is the flight of our arrows.%
}


\newcommand{\makharlancersfluff}{%
	We are the Gyula's shock cavalry. We ride larger horses than most Makhar, Kadzoly warmbloods, specially bred in the lands bordering Vetia. Wielding fearsome double-handed lances, we close with the enemy with terrifying speed, devastating our foes with bone splintering force. Either skewered by lance or smashed lifeless by flailing hooves, the role of the lancers is to decimate arrow-riddled units, sending them fleeing or to their graves.%
	\fluffref{Elac---Makhar Lancer}%
}


\newcommand{\makharflayersfluff}{%
	Among the Makhar, some follow a darker path. That of the Flayer. Where the herdsman is content with his horses and sheep, the Flayer seeks more exotic and sometimes dangerous pastoral beasts. Chimeras, turuls, karkadans, and in rare cases humans; the more dangerous the herd, the more prestigious in the eyes of a Flayer. To control these perilous and unpredictable herds, Flayers mount the most spirited creatures: Shadow Chasers.%
}


\newcommand{\makharchariotfluff}{%
	You want to know what haunts my nightmares? Thirty years I was a Reiter. Seen, fought, and killed most anything that walks, flies, or crawls. I've fought plenty of cavalry and infantry, easy kills for the repeaters, but that chariot was the worst I faced\dots{} I'll never forget it. Four warriors to deal with, two of them riding the horses\dots{} caused us a lot of problems. Either too many bows, or too many of those damned heavy lances. Lost good men that day, Ullor bless them. Now, hand me that bottle.%
	\fluffref{Sgt JG Holtz, former Reiter, now guide to the Makhar}%
}


\newcommand{\warriorknightsfluff}{%
	Makhar who have sworn themselves to the Dark Gods often return to their homes on the Steppe to fulfill their path for reasons that are unclear to even the Táltos. Nonetheless, we welcome them, as their prowess in battle is undoubted.%
}


\newcommand{\turulfluff}{%
	I am struggling to get the turul eggs you requested, Master. These creatures are smarter than eagles. When the mother goes off to hunt and I see her wings disappear over the horizon, I begin my descent. Every time I am within metres of her nest my spotter shouts down to me and I must abort the climb. It's as though the damned turul can see me from miles away! These beasts are fearsome, truly. With the hindquarters of a mountain lion and the claws, head, and wings of a giant hawk I dare not get close to the nest when she is within sight. I would be ripped to shreds. Another method must be found.%
	\fluffref{Taken from a letter found in the Gyula's Pavilion}%
}


\newcommand{\karkadanherdfluff}{%
	Our guide continues to find our ignorance amusing. Many months after we left Volskagrad, we camped the night in a rocky river basin next to a watering hole fed by a small stream. Upon awakening with the morning sun I went to stretch my legs and loose my bladder. Much to my surprise, I was confronted across the watering hole by a furry beast with a gigantic nose-horn slurping greedily. In my excitement at being the first man of Zilas to experience the majesty of a unicorn, I awoke the camp with my screams of delight. Once roused, our guide promptly dismissed my discovery and informed me of the beast's true nature. As if in agreement, the karkadan turned and released its bowels in my direction, kicking its back legs to spread its steaming faeces. With a grunt it promptly rumbled off into the tundra to join its herd.%
	\fluffref{Excerpt from the diary and travels of Columbo Vinaroni. Embassy of Zilas to the Great Khan---found in the Gyula's Pavilion}%
}


\newcommand{\nomadicgiantfluff}{%
	Some Steppe people foster relations with the wandering giants of the grasslands. Although their lumbering gait is dissimilar to our highly mobile warriors, they can be brutal in battle and in simple imitation of our archers some sport mighty bows that launch gigantic arrows of death to smash apart our foes. A fine sight indeed.%
}


\newcommand{\steppemammothfluff}{%
	Entering the valley from over a high pass, the green sea of grass spread out before us like verdant silk slung carelessly across a floor. The deep blue of the morning sky met the boundless green of the steppe. The only thing disturbing the idyllic folds of the grasslands appeared to be large boulders clumped together haphazardly. On closer inspection these boulders seemed to possess a heavy fur coat. When I remarked this to our guide he almost fell off his horse with laughter. He informed us that these boulders were in fact humongous beasts and quite approachable when grazing. However, if roused to anger, these \enquote{mamuts}, he divulged, are unstoppable behemoths of rage. They are herded and ridden in the same way as horses and their milk is fermented as a highly prized delicacy along the Makhar tribes---kumis, powerful liquor.%
	\fluffref{Excerpt from the diary and travels of Columbo Vinaroni. Embassy of Zilas to the Great Khan---found in the Gyula's Pavillion}%
}
