% Army Model Rules Names

\newcommand{\warriorvassals}{Warrior Vassals}
\newcommand{\ironrain}{Iron Rain}
\newcommand{\infernalarmour}{Infernal Armour}
\newcommand{\hobgoblinscimitar}{Hobgoblin Scimitar}
\newcommand{\flintlockaxe}{Flintlock Axe}
\newcommand{\blunderbuss}{Blunderbuss}
\newcommand{\hobcohesion}{\newrule{Hob Cohesion}}
\newcommand{\regimentalmascot}{\newrule{Regimental Mascot}}
\newcommand{\royalgogyagbarding}{\newrule{Royal Gogyag Barding}}
% Army Model Rules Texts

\newcommand{\warriorvassalsdef}{%
	The total Combat Score bonus from each player gained in Duels (from lost Health Points on enemy units and Overkill), is reduced by 1, to a minimum of 0.%
}
\newcommand{\ironraindef}{%
\newrule{If one or more of the following conditions are met, t}he Shooting Attack gains +1 to hit and \textbf{always} has at least Armour Penetration 1 \newrule{\removedrule{if one or more of the following conditions are met}}:
\begin{itemize}
	\item The attacker is located in the target's Flank or Rear Arc.
	\item The target has suffered one or more hits from \newrule{Slings} earlier in the same Shooting Phase, and no other Shooting Attack has hit the unit since then.
\end{itemize}
}

\newcommand{\infernalarmourdef}{%
	Plate Armour. The wearer gains \textbf{\aegis{} (5+, against \flamingattacks{})}.%
}
\newcommand{\infernalarmourrestriction}{(Wizard Master only)}

\newcommand{\flintlockaxedef}{%
	Counts as a Close Combat Weapon with \textbf{\twohanded} in close combat. Close Combat Attacks made with it gain +1 Strength. Can be enchanted like a Close Combat Weapon, but only Close Combat Attacks are affected by the Weapon Enchantment unless specifically stated otherwise. The model may shoot from the third rank (in addition to the first and second).%
}
\newcommand{\blunderbussdef}{%
	Does not suffer the negative to-hit modifier from a Stand and Shoot Charge Reaction.%
}
\newcommand{\hobcohesiondef}{%
	\newrule{For the purpose of receiving \commandingpresence{} and \rallyaroundtheflag{} from friendly models, the model counts as \distance{6} closer to those models.}%
}
\newcommand{\regimentalmascotdef}{%
	\newrule{The model \textbf{must} be deployed in, and can only join a \hoblevies{} unit. The model can \textbf{never} voluntarily leave its unit.}%
}
\newcommand{\royalgogyagbardingdef}{%
	\newrule{When the model suffers a wound from an attack with \multiplewounds{}, (X) halve X, rounding fractions up.}
}
\newcommand{\royalgogyagrestriction}{%
	\newrule{The model also counts towards the maximum number of \regimentalgogyag{}s allowed from Core.}
}
	