%%%% Unit entries names

% CHARACTERS

\newcommand{\satrap}{Satrap}
\newcommand{\hobgoblinconjurer}{Hobgoblin Conjurer}
\newcommand{\hobsavaran}{\newrule{Hob Savaran}}

% MOUNTS

\newcommand{\mountainwolf}{Mountain Wolf}
\newcommand{\beardog}{Bear--Dog}
\newcommand{\plainstusker}{Plains Tusker}
\newcommand{\colossalcamel}{Colossal Camel}
\newcommand{\royalgogyag}{Royal Gogyag}

% CORE

\newcommand{\hoblevies}{Hob Levies}
\newcommand{\hoblevy}{Hob Levy}
\newcommand{\regimentalgogyag}{Regimental Gogyag}
\newcommand{\gogyag}{Gogyag}
\newcommand{\drummer}{Drummer}
\newcommand{\hobauxiliaries}{Hob Auxiliaries}
\newcommand{\hobauxiliary}{Hob Auxiliary}


% SPECIAL

\newcommand{\mountainwolfcavalry}{Mountain Wolf Cavalry}
\newcommand{\hobgoblinrider}{Hobgoblin Rider}

\newcommand{\tuskermahouts}{Tusker Mahouts}
\newcommand{\hobgoblinmahout}{Hobgoblin Mahout}

\newcommand{\hobcataphracts}{Hob Cataphracts}
\newcommand{\veteran}{Veteran}

% BLOTTING THE SUN

\newcommand{\blastedplainemissaries}{Blasted Plains Emissaries}
\newcommand{\blastedplainemissariesQRS}{B. P. Emissaries}
\newcommand{\emissary}{Emissary}

\newcommand{\hobballista}{Hob Ballista}
\newcommand{\crew}{Crew}

\newcommand{\skymountainemissaries}{Sky Mountain Emissaries}
\newcommand{\skymountainemissariesQRS}{S. M. Emissaries}



%%%% Unit entries rules

%% CHARACTERS

% Satrap

\newcommand{\cavalrycommander}{\newrule{Cavalry Commander}}
\newcommand{\cavalrycommanderdef}{%
	\newrule{The model \textbf{must} take a mount. The model's unit \textbf{must} reroll any natural rolls of '1' when rolling for Charge Range in the Charge Phase.}%
}

\newcommand{\archerycommander}{\newrule{Archery Commander}}
\newcommand{\archerycommanderdef}{%
	\newrule{The model's unit gains \textbf{\quicktofire{}}.}%
}


\newcommand{\shah}{\newrule{Shah}}
\newcommand{\shahdef}{%
	\newrule{The model part gains \textbf{\hatred{}}, its Special Item allowance is increased to 200 pts, and its Discipline is \textbf{set} to 9.}%
}
\newcommand{\generalonly}{General only}
\newcommand{\shahrestriction}{\newrule{*Cannot be taken by the Battle Standard Bearer}}

% Hobgoblin Conjurer

\newcommand{\ifnotwizardapprentice}{If Wizard Adept or Master}
\newcommand{\infernallackey}{Infernal Lackey}
\newcommand{\infernallackeydef}{%
	The model gains \infernalarmour{} and \flintlockaxe{} (3+). Its Discipline is \textbf{set} to 8, and it \textbf{must} \newrule{choose} \pyromancy{} \newrule{as its Path of Magic}.%
}

% Hob Savaran
\newcommand{\loyallieutenant}{\newrule{Loyal Lieutenant}}
\newcommand{\loyallieutenantdef}{\newrule{The model \textbf{must} be deployed in a unit that contains at least one R\&F model with the same Height and Type and that does not contain any other models with \loyallieutenant. The model can \textbf{never} voluntarily leave its unit.}}



%%% CORE

%% Hob Auxiliaries

\newcommand{\boilingoil}{Boiling Oil}
\newcommand{\boilingoildef}{%
	If one or more simultaneous attacks with \boilingoil{} hit, after resolving these attacks, the target unit gains one \boilingoil{} marker. If a unit with one or more \boilingoil{} markers is targeted by Shooting Attacks with \ironrain{}, the shooting models are considered to be Located in the target's Rear Arc for the purpose of \ironrain{} (not for the purpose of other rules like Area Attack). Remove all markers from a unit when it \newrule{is hit by one or more} attacks with \ironrain{} or at the end of the Shooting Phase, whichever comes first.%
}

\newcommand{\slingers}{Slingers}
\newcommand{\slingersdef}{%
The model gains \textbf{Hard Target (1)}, \textbf{Insignificant}, \textbf{Skirmisher}, and \textbf{Sling (4+)}.%
}

\newcommand{\disciples}{Disciples}
\newcommand{\disciplesdef}{%
\newrule{The model gains \swiftstride{}.} \removedrule{Units fully composed of models with Disciples gain \textbf{\swiftstride{}} for the Charge Range roll if they are Located in the Charged unit's Flank or Rear Arc when rolling their Charge Range in the Charge Phase.} In addition, while the model's unit is Engaged with an enemy unit's Flank or Rear Facing, the model's Close Combat Attacks gain +1 to hit and +\newrule{3} Armour Penetration.%
}

\newcommand{\sling}{Sling}
\newcommand{\slingdef}{%
	The attack gains +1 Strength when shooting from Short Range.%
}

%% Regimental Gogyag

\newcommand{\giantdrum}{\newrule{Giant Drum}}
\newcommand{\giantdrumdef}{%
\newrule{The range of the model's March to the Beat, and to enemy units that are required to take a March Test due to the Regimental Gogyag's unit, are both extended to \distance{18}.}%
}


%%% SPECIAL

%% Hob Cataphracts

\newcommand{\cataphractii}{Cataphractii}
\newcommand{\cataphractiidef}{%
	The model gains Lance, Paired Weapons, Heavy Armour, Shield, and \textbf{Weapon Master}.%
}

\newcommand{\eternals}{Eternals}
\newcommand{\eternalsdef}{%
The model gains Great Weapon, Infernal Armour, and \textbf{Hatred (against Beast, Cavalry)}.%
}


%%% Blotting the Sun

%% Hob Ballista

\newcommand{\ballista}{Ballista}

%%% Sky mountain emissaries

\newcommand{\saddlecannon}{Saddle Cannon}
