
\newcommand{\daemonicmanifestations}{Daemonic Manifestations}
\newcommand{\daemonicmanifestationsInitial}{DM}

\newcommand{\daemonicmanifestationsintro}{%
Cultists armies possess an additional version of Special Items called Daemonic Manifestations. They follow the rules for Special Items, with the exception that they are not \oneofakind{} and that models cannot be affected by more than one instance of each Manifestation, unless specifically stated otherwise.%
}

%%%% Manifestations of Father Chaos
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsoffatherchaos}{Manifestations of Father\newline Chaos}

\newcommand{\dextroustentacles}{Dextrous Tentacles}
\newcommand{\livingshield}{Living Shield}
\newcommand{\chitinousscales}{Chitinous Scales}
\newcommand{\centipedelegs}{Centipede Legs}
\newcommand{\unnaturalroots}{Unnatural Roots}
\newcommand{\sorcerousantennae}{Sorcerous Antennae}
\newcommand{\markoftheeternalchampion}{Mark of the Eternal Champion}
\newcommand{\chargedtendrils}{Charged Tendrils}
\newcommand{\mirroredscales}{Mirrored Scales}
\newcommand{\darkhide}{Dark Hide}
\newcommand{\hammerhand}{Hammer Hand}
\newcommand{\ironhusk}{Iron Husk}
\newcommand{\brimstonesecretions}{Brimstone Secretions}
\newcommand{\clovenhooves}{Cloven Hooves}
\newcommand{\witheringvapour}{Withering Vapour}
\newcommand{\kaleidoscopicflesh}{Kaleidoscopic Flesh}

\newcommand{\dextroustentaclesdef}{%
The model gains +1 Agility.%
}
\newcommand{\livingshielddef}{%
The model gains \textbf{\parry}.%
}
\newcommand{\chitinousscalesdef}{%
The model gains +2 Armour, to a maximum of 3.%
}
\newcommand{\centipedelegsdef}{%
The model gains +\distance{1} Advance Rate.%
}
\newcommand{\unnaturalrootsdef}{%
A side with one or more models with Unnatural Roots Engaged in Combat at the end of the Round of Combat adds +1 to its Combat Score.%
}
\newcommand{\sorcerousantennaedef}{%
At the start of Siphon the Veil in each of your Magic Phases, choose a single model part in each unit with one or more instances of this Manifestation. The chosen model part gains \textbf{\channel{} (1)} until the end of the Magic Phase.%
}
\newcommand{\markoftheeternalchampiondef}{%
If the bearer is not a Wizard, it becomes a \textbf{\wizardapprentice} that does not select spells as normal but always knows \spellformat{\spearofinfinity}{\hereditaryspell}. If the bearer is already a Wizard, it knows \spellformat{\spearofinfinity}{} in addition to its other spells and cannot select it during Spell Selection.%
}
\newcommand{\chargedtendrilsdef}{%
At the end of Siphon the Veil, the owner is allowed to store up to 6 Veil Tokens instead of the normal 3.%
}
\newcommand{\mirroredscalesdef}{%
Each Close Combat Attack allocated towards the model for which a natural \result{1} is rolled to hit is distributed onto the attacking model's Health Pool.%
}
\newcommand{\darkhidedef}{%
The model gains \textbf{\scout{}} with the following exception: it \textbf{must} be deployed fully inside the owner's Deployment Zone, and the owner \textbf{must} have deployed at least one unit normally.%
}
\newcommand{\hammerhanddef}{%
The model gains +1 Attack Value.%
}
\newcommand{\ironhuskdef}{%
The model's Resilience is \textbf{set} to 6.%
}
\newcommand{\brimstonesecretionsdef}{%
Attacks that are \divineattacks{} made against the model lose this Attack Attribute.%
}
\newcommand{\clovenhoovesdef}{%
Unless the model already has Impact Hits (X), it gains \textbf{\impacthits{} (D3+1)}. These Impact Hits are resolved with Strength 5 and Armour Penetration 2.%
}
\newcommand{\witheringvapourdef}{%
The bearer gains \textbf{\breathattack{\St{} 3, \AP{} 2}}.%
}
\newcommand{\kaleidoscopicfleshdef}{%
The model gains \textbf{\hardtarget{} (1)}.%
}


%%%% Manifestations of Envy
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofenvy}{Manifestations of Envy}

\newcommand{\venomsacs}{Venom Sacs}
\newcommand{\greenfireeyes}{Greenfire Eyes}
\newcommand{\piercingspike}{Piercing Spike}

\newcommand{\venomsacsdef}{%
The model gains \textbf{\poisonattacks}. If the model's Close Combat Attacks already were \poisonattacks{} from another source than this Manifestation, the attack will automatically wound on successful to-hit rolls of 5+ instead of 6+.%
}
\newcommand{\greenfireeyesdef}{%
One use only. \textbf{Must} be activated when the model's unit fails its first Charge Range roll. The unit \textbf{must} reroll the Charge Range roll.%
}
\newcommand{\piercingspikedef}{%
Close Combat Attacks made by the model gain +1 Armour Penetration.%
}


%%%% Manifestations of Gluttony
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofgluttony}{Manifestations of Gluttony}

\newcommand{\unhingingjaw}{Unhinging Jaw}
\newcommand{\digestivevomit}{Digestive Vomit}
\newcommand{\broodmother}{Broodmother}

\newcommand{\unhingingjawdef}{%
Failed to-wound rolls from Close Combat Attacks against Large or Gigantic models made by the model \textbf{must} be rerolled.%
}
\newcommand{\digestivevomitdef}{%
One use only. \textbf{Must} be activated the first time the model's unit performs a Post-Combat Pivot or a Post-Combat Reform. The model gains +1 Strength and +1 Armour Penetration until the end of the game.%
}
\newcommand{\broodmotherdef}{%
At the end of each Round of Combat during which the model's unit was Engaged in Combat, and during which models with Broodmother caused at least three Health Point losses against enemy units with Close Combat Attacks, the unit Raises D3 Health Points.%
}


%%%% Manifestations of Greed
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofgreed}{Manifestations of Greed}

\newcommand{\graspingproboscis}{Grasping Proboscis}
\newcommand{\diviningsnout}{Divining Snout}
\newcommand{\smotheringcoils}{Smothering Coils}

\newcommand{\graspingproboscisdef}{%
At the end of each Round of Combat during which the model's unit was Engaged in Combat, and during which models with Grasping Proboscis caused at least three Health Point losses against enemy units with Melee Attacks, the owner gains D3 Veil Tokens to their Veil Token pool.%
}
\newcommand{\diviningsnoutdef}{%
When Charging a unit that contains one or more Special Items, the model gains +\distance{2} Advance Rate for Charge Range rolls. The effects only apply in the Charge Phase and only if all models in the unit are affected by \diviningsnout{}.%
}
\newcommand{\smotheringcoilsdef}{%
The model gains +1 to-wound with Close Combat Attacks against models with Scoring.%
}


%%%% Manifestations of Lust
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsoflust}{Manifestations of Lust}

\newcommand{\hotblood}{Hot Blood}
\newcommand{\mesmerisingplumage}{Mesmerising Plumage}
\newcommand{\roaminghands}{Roaming Hands}

\newcommand{\hotblooddef}{%
The model gains \textbf{\devastatingcharge{+2 \Ag{}}}.%
}
\newcommand{\mesmerisingplumagedef}{%
Enemy units in base contact with one or more models with this Manifestation suffer \minuss{}1 Offensive Skill and \minuss{}1 Defensive Skill.%
}
\newcommand{\roaminghandsdef}{%
While the unit is Engaged with an enemy unit's Flank or Rear Facing, the model gains +1 Strength and +1 Armour Penetration.%
}


%%%% Manifestations of Pride
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofpride}{Manifestations of Pride}

\newcommand{\hornsofhubris}{Horns of Hubris}
\newcommand{\stiffupperlip}{Stiff Upper Lip}
\newcommand{\bronzebackbone}{Bronze Backbone}

\newcommand{\hornsofhubrisdef}{%
The model gains \textbf{\vanguard{} (\distance{6})}.%
}
\newcommand{\stiffupperlipdef}{%
Discipline Tests taken by units with at least one model with this Manifestation are subject to Minimised Roll.%
}
\newcommand{\bronzebackbonedef}{%
The model gains \textbf{\hatred}.%
}


%%%% Manifestations of Sloth
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofsloth}{Manifestations of Sloth}

\newcommand{\segmentedshell}{Segmented Shell}
\newcommand{\auraofdespair}{Aura of Despair}
\newcommand{\chillingyawn}{Chilling Yawn}

\newcommand{\segmentedshelldef}{%
When the model suffers a wound from an attack with \multiplewounds{}{} (X), reduce X by 1, to a minimum of 1.%
}
\newcommand{\auraofdespairdef}{%
Enemy units suffer \minuss{}\distance{2} Advance Rate to a minimum of \distance{1} when rolling for Charge Range against units with at least one model with this Manifestation in the Charge Phase.%
}
\newcommand{\chillingyawndef}{%
Enemy units in base contact with one or more models with this Manifestation suffer \minuss{}2 Agility.%
}


%%%% Manifestations of Wrath
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofwrath}{Manifestations of Wrath}

\newcommand{\incendiaryichor}{Incendiary Ichor}
\newcommand{\whipcracktail}{Whipcrack Tail}
\newcommand{\redhaze}{Red Haze}

\newcommand{\incendiaryichordef}{%
The model gains \textbf{\aegis{} (2+, against \flamingattacks{})}. All Melee Attacks (including Special Attacks) and Shooting Attacks made by the model with \incendiaryichor{} become \textbf{\flamingattacks{}}. The model automatically fails all Fortitude Saves.%
}
\newcommand{\whipcracktaildef}{%
The model gains \textbf{\lightningreflexes{}}.%
}
\newcommand{\redhazedef}{%
The model's Close Combat Attacks gain +1 Strength and +1 Armour Penetration, but each of its Close Combat Attacks with a natural to-hit roll of \result{1} is distributed onto the attacking model's Health Pool.%
}
