
%%%% Unit entries names

% CHARACTERS

\newcommand{\cultleader}{Cult Leader}

\newcommand{\daemonsymbiote}{Daemon Symbiote}


% CORE

\newcommand{\cultist}{Cultist}
\newcommand{\cultists}{Cultists}

\newcommand{\imp}{Imp}
\newcommand{\imps}{Imps}

\newcommand{\succubus}{Succubus}
\newcommand{\succubi}{Succubi}

\newcommand{\lemures}{Lemures}
\newcommand{\lemure}{Lemure}

\newcommand{\myrmidons}{Myrmidons}
\newcommand{\myrmidon}{Myrmidon}


% SPECIAL

\newcommand{\possessed}{Possessed}
\newcommand{\possessedSINGULAR}{Possessed}

\newcommand{\ritualaltar}{Ritual Altar}

\newcommand{\profaneidol}{Profane Idol}


% DAEMONIC SUMMONS

\newcommand{\eidolons}{Eidolons}
\newcommand{\eidolon}{Eidolon}

\newcommand{\hellhounds}{Hellhounds}
\newcommand{\hellhound}{Hellhound}

\newcommand{\threshingengine}{Threshing Engine}
\newcommand{\tiller}{Tiller}
\newcommand{\draftbeast}{Draft Beast}

\newcommand{\hordethresher}{Horde Thresher}
\newcommand{\legionthresher}{Legion Thresher}

\newcommand{\titanslayerchariot}{Titanslayer Chariot}
\newcommand{\chtonicmachinator}{Chthonic Machinator}

\newcommand{\clawedfiends}{Clawed Fiends}
\newcommand{\clawedfiend}{Clawed Fiend}

\newcommand{\mageblightgremlins}{Mageblight Gremlins}
\newcommand{\mageblightgremlin}{Mageblight Gremlin}

\newcommand{\hoarders}{Hoarders}
\newcommand{\hoarder}{Hoarder}

\newcommand{\sirens}{Sirens}
\newcommand{\siren}{Siren}
\newcommand{\palesteed}{Pale Steed}

\newcommand{\blazingglory}{Blazing Glory}

\newcommand{\hopeharvester}{Hope Harvester}

\newcommand{\brazenbeasts}{Brazen Beasts}
\newcommand{\daredevil}{Daredevil}
\newcommand{\BBbeast}{\beast}% in case you want a different translation than the generic beast

\newcommand{\furies}{Furies}
\newcommand{\fury}{Fury}

\newcommand{\veilserpents}{Veil Serpents}
\newcommand{\veilserpent}{Veil Serpent}

\newcommand{\bloatflies}{Bloat Flies}
\newcommand{\bloatfly}{Bloat Fly}


%%%% Unit entries rules

%% CHARACTERS

% Cult Leader

\newcommand{\masterofritual}{Master of Ritual}
\newcommand{\masterofritualdef}{%
	The model gains +1 Discipline, \textbf{Daemonic Summon}, \textbf{\scout{}}, and its Commanding Presence range is \textbf{set} to \distance{18}.%
}

% Daemon Symbiote
\newcommand{\singlemanifestation}{A single Manifestation}

% General

\newcommand{\manifestationonechoice}[1]{%
	\exploptionschoice{Manifestation (one choice only):}{\explAlCoOrder{#1}}%
}

\newcommand{\summonedcategorynote}{%
	The unit cannot be deployed normally, but only through Daemonic Summon.%
}

%% CORE

% Cultists

\newcommand{\eldritchtome}{Eldritch Tome}
\newcommand{\eldritchtomedef}{%
	\itemrestriction{Units with Champion only.}%
	The unit gains \textbf{Wizard Conclave} that knows only \spellformat{\spearofinfinity}{\hereditaryspell}.%
}

\newcommand{\abyssalconduit}{Abyssal Conduit}
\newcommand{\abyssalconduitdef}{%
	One model in the unit that is not a Champion or Musician becomes a \textbf{Standard Bearer} with \textbf{\channel{} (1)} and \textbf{\daemonicsummon{}}.%
}

\newcommand{\infiltrators}{Infiltrators}
\newcommand{\infiltratorsdef}{%
	The model gains \textbf{\scout{}} and loses \scoring{}.%
}


% Imps

\newcommand{\impsaegis}{\aegis{} (3+, against Shooting Attacks)}

\newcommand{\energybolts}{Energy Bolts}

\newcommand{\firestarter}{Firestarter}
\newcommand{\firestarterdef}{%
	The Standard Bearer can cast the spell stated in brackets as a Bound Spell with Power Level (5/8).%
}


% Succubi

\newcommand{\talonscythes}{Talon Scythes}
\newcommand{\talonscythesdef}{%
	Attacks made with Talon Scythes ignore \parry{} and, if allocated towards Standard or Large Infantry, gain a +1 to-hit modifier.%
}


%% SPECIAL

% Ritual Altar

\newcommand{\darkconclave}{Dark Conclave}
\newcommand{\darkconclavedef}{%
	Spells cast by the model gain +\distance{3} range for each additional friendly Wizard within \distance{12} of the Caster. This bonus can never increase the combined modifier beyond +\distance{9}, however other sources may.\newline
	The model \textbf{must} select 2 spells from: \spellformat{\spearofinfinity}{\hereditaryspell}, \spellformat{\thaumaturgyspellone}{\thaumaturgy}, and \spellformat{\occultismspellsix}{\occultism} during Spell Selection. This overrides the normal Spell Selection rules connected to being a Wizard Adept.\newline
	When performing a Daemonic Summon with the model, divide the chosen unit's Point Cost by 300 (instead of 200), rounding fractions up, for determining the number of discarded Veil Tokens.%
}

\newcommand{\grandcouncil}{Grand Council}
\newcommand{\councilmembers}{Council Members}
\newcommand{\grandcouncildef}{%
	The model's Health Points and Attack Value are \textbf{set} to 8, and its base size is changed to 120 mm round.
	The model can also select \spellformat{\thaumaturgyspellfive}{\thaumaturgy} as one of its 2 spells.%
}

% Profane Idol

\newcommand{\doomsdaycolossus}{Doomsday Colossus}
\newcommand{\doomsdaycolossusdef}{%
	The model's Health Points are \textbf{set} to 8, and its base size is changed to 75\timess{}100 mm. The roll for the number of hits from its Stomp Attacks is subject to Maximised Roll.%
}

\newcommand{\apostateautomaton}{Apostate Automaton}
\newcommand{\apostateautomatondef}{%
	The model gains +1 Resilience, \textbf{Crush Attack}, and its Armour is \textbf{set} to 3.%
}

\newcommand{\hereticgolem}{Heretic Golem}
\newcommand{\hereticgolemdef}{%
	The model gains +1 Strength and +1 Armour Penetration.%
}

\newcommand{\wickerman}{Wicker Man}
\newcommand{\wickermandef}{%
	The model gains \textbf{Flammable}, \textbf{Flaming Attacks}, and \textbf{\grindattacks{3D3}}. These Grind Attacks are resolved with Strength 4, Armour Penetration 0, and Flaming Attacks.
}

%% DAEMONIC SUMMONS

% Eidolons

\newcommand{\darkfire}{Dark Fire}
\newcommand{\darkfiredef}{%
Armour Save rolls of \result{1}, \result{2}, \result{3}, and \result{4} are \textbf{always} considered failed when saving wounds caused by \darkfire{}.%
}

% Hellhounds

\newcommand{\hellishgrowl}{Hellish Growl}
\newcommand{\hellishgrowldef}{%
	At the start of each Round of Combat, enemy units in base contact with one or more models with Hellish Growl \textbf{must} take a Discipline Test with a \minuss{}1 modifier.\par%
	Failed to-wound rolls from attacks made by the model against units that fail this test \textbf{must} be rerolled. The effect lasts until the end of the Round of Combat.%
}

% Threshing Engine

\newcommand{\flycategorynote}{The unit also counts towards Aves if taking Fly.}
\newcommand{\chassis}{Chassis}
\newcommand{\colossalstature}{Colossal Stature}
\newcommand{\colossalstaturedef}{The model counts as Gigantic for the purpose of determining the number of Full Ranks.}

\newcommand{\hordethresherdef}{%
	Changes to the model's profile:
	\begin{itemize}
		\item Its base size is changed to \textbf{100\timess{}\SI{100}{\milli\meter}}.
		\item Its Health Points are \textbf{set} to \textbf{6}.
		\item It gains \textbf{1} additional Tiller.
		\item It gains \textbf{1} additional Draft Beast.
		\item It gains \textbf{\colossalstature{}}.
		\item The Chassis gains \textbf{\impacthits{3D3}}.
	\end{itemize}%
}
\newcommand{\legionthresherdef}{%
	Changes to the model's profile:
	\begin{itemize}
		\item Its base size is changed to \textbf{100\timess{}\SI{150}{\milli\meter}}.
		\item Its Health Points are \textbf{set} to \textbf{8}.
		\item It gains \textbf{2} additional Tillers.
		\item It gains \textbf{2} additional Draft Beasts.
		\item It gains \textbf{\colossalstature{}}.
		\item The Chassis gains \textbf{\impacthits{4D3}}.
	\end{itemize}%
}

% Titanslayer Chariot

\newcommand{\mountainbreaker}{Mountain Breaker}
\newcommand{\mountainbreakerdef}{%
	The model gains +\distance{2} Advance Rate when rolling for Charge Range against units that consist entirely of models with Towering Presence in the Charge Phase. In addition, the model's Impact Hits gain \textbf{\multiplewounds{}{} (D3, against \toweringpresence{})}.%
}

% Clawed Fiends

\newcommand{\smother}{Smother}
\newcommand{\smotherdef}{%
	If the attack is allocated towards a Large model, it gains +1 to hit and +1 to wound.%
}

% Mageblight Gremlins

\newcommand{\spellcraving}{Spell Craving}
\newcommand{\spellcravingdef}{%
	The model can perform up to 3 Supporting Attacks. When determining Combat Score, a side with at least one model with Spell Craving Engaged in Combat adds +X to its side's Combat Score, where X is the number of non-Bound non-Attribute Spells known by enemy Wizards in units in base contact with it (note that multiple instances of the same spell count as 1 each).%
}

\newcommand{\veilstalker}{Veil Stalker}
\newcommand{\veilstalkerdef}{%
	The model follows the rules for Ambush with the following exceptions:\newline
	When the unit arrives, the owner may choose to place it within \distance{6} of an enemy model with \channel{} (instead of entering the Battlefield from the Board Edge). If so, it cannot perform any Advance Moves this Movement Phase (note that this does not prevent the unit from performing a Reform).%
}

% Hoarders

\newcommand{\tighteninggrasp}{Tightening Grasp}
\newcommand{\tighteninggraspdef}{%
	The model gains \textbf{\grindattacks{X}}, and can make \grindattacks{} as Supporting Attacks, ignoring the maximum number of Supporting Attacks. When the model is not Engaged in Combat, X is \textbf{set} to 1.\par%
	At the start of each Round of Combat other than the First Round of Combat, if the model is Engaged, X is increased by +1 (e.g. \grindattacks{1} becomes \grindattacks{2}).%
}

\newcommand{\uptotwomanifestations}[1]{%
	\exploptionschoice{Up to two Manifestations:}{\explAlCoOrder{#1}}%
}

% Sirens

\newcommand{\symbioticsteed}{Symbiotic Steed}
\newcommand{\elusive}{Elusive}
\newcommand{\elusivedef}{%
	Units composed entirely of models with Elusive may declare a Flee Charge Reaction despite being Fearless.%
}

% Blazing Glory

\newcommand{\fallingstar}{Falling Star}
\newcommand{\fallingstardef}{%
	The model's Offensive Skill and Defensive Skill are \textbf{set} to twice the model's current number of Health Points.\newline
	The model counts as a Character for the purpose of issuing, accepting, and refusing Duels. When the model fights a Duel during a Round of Combat, it gains \textbf{Stubborn} until the end of the Round of Combat.%
}

% Hope Harvester

\newcommand{\aetherbattery}{Aether Battery}
\newcommand{\aetherbatterydef}{%
	Before rolling for the number of shots, the owner may choose to discard 1--3 Veil Tokens from their Veil Token pool. If so, the number of shots is increased by +3 per discarded Veil Token.%
}


%% AVES

% Veil Serpents

\newcommand{\manifestation}{Manifestation}
\newcommand{\optionalmanifestation}{Optional Manifestation}
\newcommand{\writhingnightmares}{Writhing Nightmares}
\newcommand{\writhingnightmaresdef}{%
	Enemy units in base contact with one or more models with Writhing Nightmares suffer \minuss{}1 Discipline.%
}
\newcommand{\morphlings}{Morphlings}
\newcommand{\morphlingsdef}{%
	During Spell Selection, each unit of Veil Serpents \textbf{must} choose a Manifestation from the list below and apply the effects during the game.%
}

% Bloat Flies

\newcommand{\boatfliesaegis}{\aegis{} (5+, against \magicalattacks{})}

\newcommand{\acidblood}{Acid Blood}
\newcommand{\acidblooddef}{%
	For each Fortitude Save the model fails against Melee Attacks, the model immediately inflicts 1 hit with \toxicattacks{} against the model that caused the wound, before any casualties are removed, distributed onto the model's Health Pool.%
}
