%knightly principles names

\newcommand{\knightlyprinciples}{Knightly Principles}%
\newcommand{\knightlyprinciple}{Knightly Principle}%
\newcommand{\knightlyprinciplesInitial}{KP}%

\newcommand{\excellence}{Excellence}%
\newcommand{\forbearance}{Forbearance}%
\newcommand{\generosity}{Generosity}%
\newcommand{\justice}{Justice}%
\newcommand{\valour}{Valour}%
\newcommand{\honour}{Honour}%
\newcommand{\faith}{Faith}%

%knightly principles definitions

\newcommand{\excellencerestriction}{\oneofakind{}}%
\newcommand{\excellencedef}{%
	Duels issued by the model \textbf{must} (if possible) be accepted by an enemy Character, unless a Champion accepts first. In addition, while fighting a Duel, the model part's Close Combat Attacks gain +2 Armour Penetration.%
}%

\newcommand{\forbearancerestriction}{\oneofakind{}}%
\newcommand{\forbearancedef}{%
	While using a \shield{}, the model gains \textbf{Distracting}. %
}%

\newcommand{\generosityrestriction}{\oneofakind{}}%
\newcommand{\generositydef}{%
	The model gains \textbf{\attached{}} and \textbf{\exclusive{}} (\rnf{} model). \rnf{} models with \courage{} in the unit that the model is deployed in gain \bastardsword{} and \textbf{\weaponmaster{}} until the end of the game.%
}%

\newcommand{\justicerestriction}{\oneofakind{}}%
\newcommand{\justicedef}{%
	Whenever another model in the model's unit suffers an unsaved wound due to an enemy Melee Attack (including Initiative Step 0), the model part \textbf{must} perform a single Close Combat Attack at Initiative Step 0 against an enemy model in base contact. If this is not possible, the effect is ignored. The number of these bonus attacks that the model part performs can \textbf{never} be higher than 3 per Round of Combat.%\columnbreak%
}%

\newcommand{\valourrestriction}{\oneofakind{}}%
\newcommand{\valourdef}{%
	The model gains \textbf{\fearless{}} and the model part's Close Combat Attacks gain \textbf{Multiple Wounds (2, against Fear)}.%\columnbreak%
}%

\newcommand{\honourrestriction}{\oneofakind{}}%
\newcommand{\honourdef}{%
	The model \newrule{gains \textbf{\maximised{Charge Range}}}\removedrule{'s rolls for Charge Range are subject to Maximised Roll}. \newline%
	In addition, while Engaged with an enemy unit's Front Facing, the model part gains \textbf{Devastating Charge (+2 Att)}.%
}%

\newcommand{\faithrestriction}{\oneofakind{}}%
\newcommand{\faithdef}{%
	The model \newrule{gains \textbf{Ordained}} \removedrule{\textbf{\divineattacks{}}}. In addition, if the model's unit is the target of an Orison while Engaged in Combat, add one \blessing{} Token to the owner's \blessing{} Token pool. %
}%
