
%%UNIT NAMES
%% CHARACTERS
\newcommand{\marshal}{Marshal}

\newcommand{\kncdr}{Knight Commander}

\newcommand{\prelate}{Prelate}

\newcommand{\eoswizard}{Wizard}

\newcommand{\artificer}{Artificer}

\newcommand{\inquisitor}{Inquisitor}

%% MOUNTS
\newcommand{\pegasus}{Pegasus}

\newcommand{\horse}{Horse}

\newcommand{\younggriff}{Young Griffon}

\newcommand{\greatgriff}{Great Griffon}

\newcommand{\dragon}{Dragon}

\newcommand{\arcengine}{Arcane Engine}
\newcommand{\chassis}{Chassis}
\newcommand{\crew}{Crew}

\newcommand{\altbattle}{Altar of Battle}

%% CORE
\newcommand{\hvyinf}{Heavy Infantry}
\newcommand{\hvyinfSINGULAR}{Heavy Infantry}

\newcommand{\ltinf}{Light Infantry}
\newcommand{\ltinfSINGULAR}{Light Infantry}

\newcommand{\statemilitia}{State Militia}
\newcommand{\statemilitiaSINGULAR}{State Militia}

\newcommand{\eleccav}{Electoral Cavalry}
\newcommand{\knight}{Knight}
\newcommand{\knightlyorders}{Knightly Orders}

%% SPECIAL
\newcommand{\impguard}{Imperial Guard}
\newcommand{\impguardSINGULAR}{Imperial Guard}

\newcommand{\knsun}{Knights of the Sun Griffon}
\newcommand{\knsunQRS}{Kn. of the Sun Griffon}

%% IMP AUX
\newcommand{\imprgrs}{Imperial Rangers}
\newcommand{\imprgr}{Imperial Ranger}

\newcommand{\reiters}{Reiters}
\newcommand{\reiter}{Reiter}

%% IMP ARM
\newcommand{\arty}{Artillery}

%%SUNNA FURY
\newcommand{\flagellants}{Flagellants}
\newcommand{\flagellant}{Flagellant}

\newcommand{\stank}{Steam Tank}
\newcommand{\steelram}{Steel Ram}

%% UNIT RULES ENTRIES
% CHARACTERS
% MARSHAL

\newcommand{\ifbsb}{If \bsb{}}
\newcommand{\greatgriffonrestriction}{Cannot be taken by the \bsb{}.}
\newcommand{\greattac}{Great Tactician}
\newcommand{\greattacdef}{%
	The model may give two Orders per turn instead of one.%
}

\newcommand{\impprince}{Imperial Prince}
\newcommand{\impprincedef}{%
	The model part gains +1 Attack Value, is equipped with a Hand Weapon enchanted with \textbf{The Light of Sonnstahl}, and may only take up to 50 pts of Special Items.%
}

%KNIGHT CDR
\newcommand{\firstkn}{First Knight}
\newcommand{\firstkndef}{%
	While the model is joined to a unit of Knightly Orders, the unit gains the following rules:
	\begin{itemize}%
		\item \textbf{Fearless}.%
		\item If the model is the General, the \rnf{} models also gain \textbf{Parent Unit}.%
	\end{itemize}%
}

\newcommand{\musttakeamount}{\textbf{Must} take a mount}
\newcommand{\seemount}{see mount}

%ARTIFICER
\newcommand{\mstart}{Master Artificer}
\newcommand{\mstartdef}{%
	The Master Artificer may give the Order \textbf{Ready! Aim! Fire!} to a Parent Unit or Support Unit it has joined.%
}

%INQ
\newcommand{\blessedsteel}{Blessed Steel}
\newcommand{\blessedsteeldef}{%
	The model part gains +2 Agility. Close Combat Attacks made by the model part gain +1 Strength and +1 Armour Penetration.%
}

\newcommand{\silvershotscountsas}{If taking \textbf{Silver Shots}, the unit also counts towards \impaux{}.}

\newcommand{\silvershots}{Silver Shots}
\newcommand{\silvershotsdef}{%
	The attack gains \textbf{Lethal Strike}, \textbf{Multiple Wounds (D3)}, and \textbf{must} reroll failed to-wound rolls.%
}

% MOUNTS
%Dragon
\newcommand{\eosmeetingofmindsdef}{%
	The model may give two Orders per turn instead of one.
}

\newcommand{\holyrelic}{Holy Relic}
\newcommand{\holyrelicdef}{%
	Friendly units within \distance{8} of the model gain \textbf{Hatred}. Model parts with Harnessed are not affected. For Bound Spells from Blessings cast by the rider, Type: Caster's Unit is replaced with Type: \distance{8} Aura. The model can cast \spellformat{\divinationspellfive}{\divination} as a Bound Spell with Power Level (4/8).%
}

%ARCANE ENGINE
\newcommand{\arcanesh}{Arcane Shield}
\newcommand{\arcaneshdef}{%
	Friendly units within \distance{8} of the model gain \textbf{Distracting}. The model can cast \spellformat{\cosmologyspellfour}{\cosmology} as a Bound Spell with Power Level (4/8).%
}

\newcommand{\foresight}{Foresight}
\newcommand{\foresightdef}{%
	Friendly units within \distance{8} of the model gain \textbf{Lightning Reflexes}. The model can cast \spellformat{\cosmologyspellthree}{\cosmology} as a Bound Spell with Power Level (4/8).%
}

% CORE

% HVY INF
\newcommand{\hvyinfconditionforparent}{If starting size is 21 or more models.}
\newcommand{\hvyinfconditionforsupport}{If starting size is 20 models.}

% LT INF
\newcommand{\replacecrossbowhandgunwitheither}{Replace Shooting Weapon with either}

% STATE MILITIA
\newcommand{\reserves}{Reserves}
\newcommand{\reservesdef}{%
	The unit is treated as \textbf{Insignificant} by Parent and Support Units.%
}

\newcommand{\irregulars}{Irregulars}
\newcommand{\irregularsdef}{%
	The model gains \textbf{\hardtarget{} (1)} and \textbf{\skirmisher{}}.%
}

%electoral cavalry
\newcommand{\electoralcavalrynote}{* For each unit of \knightlyorders\ in the army, the maximum number is reduced by 1.}

%knightly orders
\newcommand{\knightlyordersnote}{*0-4 Units/Army if the army includes a Knight Commander.}


% SPECIAL

% IMP AUX
%IMP RANGERS
\newcommand{\frontiersmen}{Frontiersmen}
\newcommand{\frontiersmendef}{%
	The model automatically passes Panic Tests caused by Terror.%
}

\newcommand{\beasthunters}{Beast Hunters}
\newcommand{\beasthuntersdef}{%
	When using a Bow, the Shooting Attack gains \textbf{Lethal Strike (against Beast)} and \shots{2}.%
}

%REITERS
\newcommand{\fireimpact}{Fire on Impact!}
\newcommand{\fireimpactdef}{%
	A Charging model part with Fire on Impact! using a Pistol or a Brace of Pistols \textbf{always} strikes at Initiative Step 10, and the Strength of its Close Combat Attacks is \textbf{always} set to 4 and their Armour Penetration is \textbf{always} set to 2.%
}

% IMP ARM
% BLACK POWDER ARTY
% VOLLEY GUN
\newcommand{\impvolleygun}{Volley Gun}

% MORTAR
\newcommand{\impmortar}{Mortar}

% CANNON
\newcommand{\impcannon}{Cannon}
\newcommand{\impcannondef}{%
	This Artillery Weapon can be fired in two ways:%
}

% ROCKETEER
\newcommand{\improcket}{Imperial Rocketeer}
\newcommand{\improcketdef}{%
	This weapon treats all results on the Misfire Table as Malfunction (each shot can cause a Misfire).%
}

%SUNNA FURY
%FLAGELLANTS
\newcommand{\fanatical}{Fanatical}
\newcommand{\fanaticaldef}{%
	When a model with Fanatical is killed by a Melee Attack during any Initiative Step of a Round of Combat it is fighting, remove it as a casualty only at the end of Initiative Step 0.%
}

\newcommand{\zealots}{Zealots}
\newcommand{\zealotsdef}{%
	Prelates may join the unit and gain \textbf{Fearless} and \textbf{Unbreakable} while joined to the unit.%
}

%STANK
\newcommand{\stankcannon}{Steam Cannon}

\newcommand{\steampowered}{Steam Powered}
\newcommand{\steampowereddef}{%
	The model may choose not to move despite having Random Movement,  it \textbf{always} passes Restrain Pursuit Tests, and its Pursuit and Overrun Distance in the Melee Phase are \textbf{always} \distance{0}.
	In the Movement Phase, the model's Pursuit Distance rolls are subject to Maximised Roll.%
	%
}
