
\newcommand{\daemonicmanifestations}{Daemonic Manifestations}
\newcommand{\daemonicmanifestationsInitial}{DM}

\newcommand{\daemonicmanifestationsintro}{%
Daemon Legions armies cannot pick from the list of Common Special Items. Instead, they have their own version of Special Items called Daemonic Manifestations. They follow the rules for Special Items, with the exception that they are not \oneofakind{} and that models cannot be affected by more than one instance of each Manifestation, unless specifically stated otherwise.%
}

\newcommand{\guidingmanifestations}{Guiding Manifestations}
\newcommand{\guidingmanifestationsdef}{%
Some Daemonic Manifestations have an option to be taken as a Guiding version that can only be taken by Characters. Unless specifically stated otherwise, the normal version of Manifestations is taken.  If the Guiding version is taken, this \textbf{must} be noted on your Army List. Follow the rules stated \guidingversion{with this colour-coding} and ignore Point Costs written in the standard way. Otherwise, follow the Manifestation's normal rules. In addition, all \rnf{} models in the model's unit gain the corresponding Manifestation. Note that Guiding and non-Guiding Manifestations are considered to be the same Manifestation for the purpose of Duplication Limits.%
}

%%%% Manifestations of Father Chaos
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsoffatherchaos}{Manifestations of Father Chaos}

\newcommand{\dextroustentacles}{}
\newcommand{\livingshield}{Living Shield}
\newcommand{\chitinousscales}{Chitinous Scales}
\newcommand{\centipedelegs}{Centipede Legs}
\newcommand{\unnaturalroots}{Unnatural Roots}
\newcommand{\markoftheeternalchampion}{Mark of the Eternal Champion}
\newcommand{\chargedtendrils}{}
\newcommand{\mirroredscales}{Mirrored Scales}
\newcommand{\darkhide}{Dark Hide}
\newcommand{\hammerhand}{Hammer Hand}
\newcommand{\ironhusk}{Iron Husk}
\newcommand{\brimstonesecretions}{Brimstone Secretions}
\newcommand{\clovenhooves}{}
\newcommand{\witheringvapour}{}
\newcommand{\kaleidoscopicflesh}{Kaleidoscopic Flesh}

\newcommand{\dextroustentaclesdef}{%
%
}
\newcommand{\livingshielddef}{%
The model  gains \textbf{\parry}.%
}
\newcommand{\chitinousscalesdef}{%
The model gains +2 Armour, to a maximum of 3.%
}
\newcommand{\centipedelegsdef}{%
The model  gains +\distance{2} March Rate %
}
\newcommand{\unnaturalrootsdef}{%
A side with one or more models with Unnatural Roots Engaged in Combat when Combat Scores are calculated adds +1 to its Combat Score.%
}

\newcommand{\markoftheeternalchampiondef}{%
If the bearer is not a Wizard, it becomes a \textbf{\wizardapprentice} that does not select spells as normal but always knows \spellformat{\spearofinfinity}{\hereditaryspell}. If the bearer is already a Wizard, it knows \spellformat{\spearofinfinity}{} in addition to its other spells and cannot select it during Spell Selection.%
}
\newcommand{\chargedtendrilsdef}{%
%
}
\newcommand{\mirroredscalesdef}{%
Each Close Combat Attack allocated towards the model  for which a natural \result{1} is rolled to hit is distributed onto the attacking model's Health Pool.%
}
\newcommand{\darkhidedef}{%
The model gains \textbf{\scout{}} with the following exception: it \textbf{must} be deployed fully inside the owner's Deployment Zone, and the owner \textbf{must} have deployed at least one unit normally.%
}
\newcommand{\hammerhanddef}{%
The model gains +1 Attack Value.%
}
\newcommand{\ironhuskdef}{%
The model's Resilience is \textbf{set} to 6.%
}
\newcommand{\brimstonesecretionsdef}{%
The model gains \textbf{\immune{} (\divineattacks{})}.
%
}
\newcommand{\clovenhoovesdef}{%
%
}
\newcommand{\witheringvapourdef}{%
%
}
\newcommand{\kaleidoscopicfleshdef}{%
The model  gains \textbf{\hardtarget{} (1)}.%
}


%%%% Manifestations of Envy
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofenvy}{Manifestations of Envy}

\newcommand{\venomsacs}{Venom Sacs}
\newcommand{\greenfireeyes}{Greenfire Eyes}
\newcommand{\piercingspike}{Piercing Spike}

\newcommand{\venomsacsdef}{%
The model  gains \textbf{\poisonattacks}. If the model's Close Combat Attacks  already were \poisonattacks{} from another source than this Manifestation,  they wound automatically  on a successful natural to-hit roll of '5' or '6', unless the target has \textbf{\immune\ (\poisonattacks)}.%
}
\newcommand{\greenfireeyesdef}{%
Units  containing one or more models with \greenfireeyes{} \textbf{must} reroll any natural rolls of \result{1} when rolling for Charge Range and Pursuit Distance.
%
}
\newcommand{\piercingspikedef}{%
Close Combat Attacks made by the model  gain +1 Armour Penetration.%
}


%%%% Manifestations of Gluttony
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofgluttony}{Manifestations of Gluttony}

\newcommand{\unhingingjaw}{Unhinging Jaw}
\newcommand{\digestivevomit}{Digestive Vomit}
\newcommand{\broodmother}{Broodmother}

\newcommand{\unhingingjawdef}{%
Failed to-wound rolls from Close Combat Attacks against Large or Gigantic models made by the model  \textbf{must} be rerolled.%
}
\newcommand{\digestivevomitdef}{%
	 If the model has previously been on the winning side of a combat while having this Manifestation, it gains +1 Strength and +1 Armour Penetration. %
}
\newcommand{\broodmotherdef}{%
For each Health Point loss the model causes with Close Combat Attacks against enemy units, roll a D6 at the end of the Initiative Step. For each rolled 6+, the model's Health Pool Raises 1 Health Point.%
}


%%%% Manifestations of Greed
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofgreed}{Manifestations of Greed}

\newcommand{\graspingproboscis}{}
\newcommand{\diviningsnout}{Divining Snout}
\newcommand{\smotheringcoils}{Smothering Coils}
\newcommand{\segmentedshell}{Segmented Shell}

\newcommand{\graspingproboscisdef}{%
%
}
\newcommand{\diviningsnoutdef}{%
The model  gains \textbf{\devastatingcharge{+\distance{2} Adv}} for Charges against units that contain at least one Special Item. The effects only apply if all models in the unit are affected by \diviningsnout{}.%
}
\newcommand{\smotheringcoilsdef}{%
The model  gains +1 to-wound with Close Combat Attacks against models with Scoring.%
}
\newcommand{\segmentedshelldef}{%
	When the model  suffers a wound from an attack with \multiplewounds{X}{}, reduce X by 1, to a minimum of 1.%
}
%%%% Manifestations of Lust
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsoflust}{Manifestations of Lust}

\newcommand{\hotblood}{Hot Blood}
\newcommand{\mesmerisingplumage}{Mesmerising Plumage}
\newcommand{\roaminghands}{Roaming Hands}

\newcommand{\hotblooddef}{%
The model  gains \textbf{\devastatingcharge{+2 \Ag{}}}.\columnbreak%
}
\newcommand{\mesmerisingplumagedef}{%
Enemy units in base contact with one or more models with this Manifestation suffer \minuss{}1 Offensive Skill and \minuss{}1 Defensive Skill.%
}
\newcommand{\roaminghandsdef}{%
While the unit is Engaged with an enemy unit's Flank or Rear Facing, the model  gains +1 Strength and +1 Armour Penetration.%
}


%%%% Manifestations of Pride
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofpride}{Manifestations of Pride}

\newcommand{\hornsofhubris}{Horns of Hubris}
\newcommand{\stiffupperlip}{Stiff Upper Lip}
\newcommand{\bronzebackbone}{Bronze Backbone}

\newcommand{\hornsofhubrisdef}{%
The model  gains \textbf{\vanguard{} (\distance{6})}.%
}
\newcommand{\stiffupperlipdef}{%
Units with at least one model with this Manifestation gain \textbf{\minimised{Discipline Tests}}.%
}
\newcommand{\bronzebackbonedef}{%
The model  gains \textbf{\hatred}.%
}


%%%% Manifestations of Sloth
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofsloth}{Manifestations of Sloth}


\newcommand{\auraofdespair}{Aura of Despair}
\newcommand{\chillingyawn}{Chilling Yawn}
\newcommand{\sorcerousantennae}{Sorcerous Antennae}

\newcommand{\auraofdespairdef}{%
The model gains \textbf{Accurate}.
 %
}
\newcommand{\chillingyawndef}{%
Enemy units in base contact with one or more models with this Manifestation suffer \minuss{}2 Agility.%
}

\newcommand{\sorcerousantennaedef}{%
	At the start of Siphon the Veil in each of your Magic Phases, choose a single model part in each unit with one or more instances of this Manifestation. The chosen model part gains \textbf{\channel{} (1)} until the end of the Magic Phase.%
}

%%%% Manifestations of Wrath
%%%%%%%%%%%%%%%%%%%

\newcommand{\manifestationsofwrath}{Manifestations of Wrath}

\newcommand{\incendiaryichor}{Incendiary Ichor}
\newcommand{\whipcracktail}{Whipcrack Tail}
\newcommand{\redhaze}{Red Haze}

\newcommand{\incendiaryichordef}{%
The model  gains \textbf{\aegis{3+, against \flamingattacks{}}}. All Melee Attacks (including Special Attacks) and Shooting Attacks made by the model with \incendiaryichor{} become \textbf{\flamingattacks{}}. The model  automatically fails all Fortitude Saves.%
}
\newcommand{\whipcracktaildef}{%
The model  gains \textbf{\lightningreflexes{}}.%
}
\newcommand{\redhazedef}{%
The model's Close Combat Attacks gain +1 Strength and +1 Armour Penetration, but each of its Close Combat Attacks with a natural to-hit roll of \result{1} is distributed onto the attacking model's Health Pool.%
}
