
% Special Equipment Names

\newcommand{\godslayer}{Godslayer}
\newcommand{\scourgeofkings}{Scourge of Kings}

\newcommand{\jackalsblessing}{Jackal's Blessing}
\newcommand{\sunsembrace}{Sun's Embrace}

\newcommand{\banneroftheentombed}{Banner of the Entombed}

\newcommand{\crownofthepharaohs}{Crown of the Pharaohs}
\newcommand{\sacredhourglass}{Sacred Hourglass}
\newcommand{\bookofthedead}{Book of the Dead}
\newcommand{\steedsofnephetra}{Steeds of Nephet-Ra}
\newcommand{\sekhemsceptre}{Sekhem Sceptre}
\newcommand{\blessedwrappings}{Blessed Wrappings}
\newcommand{\ankhofnaptesh}{Ankh of Naptesh}
\newcommand{\sandstormcloak}{Sandstorm Cloak}
\newcommand{\deathmaskofteput}{Death Mask of Teput}
\newcommand{\scrollofdesiccation}{Scroll of Desiccation}

% Special Equipment Texts

\newcommand{\godslayerdef}{%
	The wielder gains +1 Attack Value while using this weapon. Attacks made with this weapon become \textbf{\divineattacks} and gain \textbf{\multiplewounds{2}{\against{} \aegis{X}}} (note that the latter also applies against models with Aegis Saves with Conditional Application).%
}

\newcommand{\scourgeofkingsdef}{%
	While using this weapon, the wielder's Attack Value is \textbf{set} to 6. When fighting a Duel, attacks made with this weapon \textbf{must} reroll failed to-wound rolls.%
}

\newcommand{\jackalsblessingdef}{%
	The wearer gains +2 Health Points and \textbf{\fortitude{5+}}.%
}

\newcommand{\sunsembracedef}{%
	The bearer gains \textbf{\distracting} while using this \shield{}.%
}

\newcommand{\banneroftheentombedrestriction}{Core and Battle Standard Bearer only}
\newcommand{\banneroftheentombeddef}{%
If taken by a Character, the bearer gains  \textbf{\UDambush}. If taken by a \rnf{} model, the bearer’s unit gains \textbf{\UDambush{}} and additional models cannot be added to the unit during Army List creation. Standard Height models using this banner to Ambush must arrive in a formation containing exactly 5 models per rank (except for the last) and cannot make a Reform (or a Swift Reform) during this Player Turn.\newline
Units with  \UDambush{} also count towards \entombed.
}

\newcommand{\crownofthepharaohsrestriction}{Pharaohs and Nomarchs only}
\newcommand{\crownofthepharaohsdef}{%
	The bearer gains \textbf{\commandingpresence{}~(\distance{+6})}.
	At the start of each of your Player Turns, the bearer may lose \undyingwill{} until the start of your next Player Turn and choose a friendly unit within \distance{12}.
	This unit gains \textbf{\undyingwill{}} until the start of your next Player Turn.%
}

\newcommand{\sacredhourglassdef}{%
	The bearer may reroll the first failed Casting Attempt of a spell of type Augment in each Magic Phase that  was rolled using 2 Magic Dice (by rerolling both Magic Dice).%
}

\newcommand{\bookofthedeaddef}{%
	The bearer can cast \spellformat{\deathisonlythebeginning}{} as a Bound Spell with Power Level (4/8) and the following modification:\newline
	\nameindent{}The spell's range is changed to \distance{12} Aura.\newline
	The spell may target units containing one or more models with \ensouledstatue.
}

\newcommand{\steedsofnephetradef}{%
	Models with at least one Skeletal Horse model part in the bearer's unit gain \textbf{\ghoststep} and +\distance{4} March Rate.%
}

\newcommand{\sekhemsceptredef}{%
	The bearer gains \textbf{\autonomous} and \textbf{\stubborn}.%
}

\newcommand{\blessedwrappingsdef}{%
	The bearer gains +1 Health Point and loses Flam\-ma\-ble if it had it (note that this does not prevent the model from gaining Flammable from other sources).%
}

\newcommand{\ankhofnapteshdef}{%
	The bearer gains \textbf{\hierophant} and can never lose it. \rnf{} models in the bearer's unit gain \textbf{\fortitude{} (6+)}.%
}

\newcommand{\sandstormcloakdef}{%
	The bearer gains \textbf{\fly{5}{15}}, \textbf{\lighttroops{}}, and \textbf{\swiftstride{}}, and can perform a \textbf{\sweepingattack{}} that causes 2D6 hits with Strength 2 and Armour Penetration 1.%
%/columnbreak
}

\newcommand{\deathmaskofteputdef}{%
	Enemy units in base contact with the bearer suffer \minuss{}2 Offensive Skill.%
}

\newcommand{\scrollofdesiccationdef}{%
	After determining Deployment Zones (at the end of step 6 of the Pre-Game Sequence), choose a Field, Forest, or Water Terrain Feature. This Terrain Feature ceases to be the Terrain Feature it used to be and loses all its rules. It is treated as Dangerous Terrain~(1) for all enemy units.%
}
