
%%%% Unit entries names

% CHARACTERS

\newcommand{\dreadprince}{Dread Prince}
\newcommand{\beastmaster}{Beastmaster}
\newcommand{\silexianofficer}{Silexian Officer}
\newcommand{\templeexarch}{Temple Exarch}
\newcommand{\warlockoutcast}{Warlock Outcast}
\newcommand{\silentassassin}{Silent Assassin}

% MOUNTS

\newcommand{\elvenhorse}{Elven Horse}
\newcommand{\daebraptor}{Daeb Raptor}
\newcommand{\blackmanepegasus}{Blackmane Pegasus}
\newcommand{\raptorchariot}{Raptor Chariot}
\newcommand{\crew}{Crew}
\newcommand{\chassis}{Chassis}
\newcommand{\manticore}{Manticore}
\newcommand{\imperiousdragon}{Imperious Dragon}

% CORE

\newcommand{\silexianspears}{Silexian Spears}
\newcommand{\silexianspear}{Silexian Spear}

\newcommand{\silexianauxiliaries}{Silexian Auxiliaries}
\newcommand{\silexianauxiliary}{Silexian Auxiliary}

\newcommand{\corsairs}{Corsairs}
\newcommand{\corsair}{Corsair}

\newcommand{\beastbreakers}{Beast Breakers}
\newcommand{\beastbreaker}{Beast Breaker}

\newcommand{\templemilitants}{Temple Militants}
\newcommand{\templemilitant}{Temple Militant}

% SPECIAL

\newcommand{\obsidianguard}{Obsidian Guard}
\newcommand{\obsidianguardSINGULAR}{Obsidian Guard}

\newcommand{\judicators}{Judicators}
\newcommand{\judicator}{Judicator}

\newcommand{\dreadknights}{Dread Knights}
\newcommand{\dreadknight}{Dread Knight}
\newcommand{\knight}{Knight}

\newcommand{\harpies}{Harpies}
\newcommand{\harpy}{Harpy}

\newcommand{\gorgons}{Gorgons}
\newcommand{\gorgon}{Gorgon}

\newcommand{\thunderpack}{Thunder Pack}
\newcommand{\thunderbeast}{Thunder Beast}
\newcommand{\lashmaster}{Lashmaster}

\newcommand{\warlockacolytes}{Warlock Acolytes}
\newcommand{\warlockacolyte}{Warlock Acolyte}
\newcommand{\acolyte}{Acolyte}

\newcommand{\divinealtar}{Divine Altar}
\newcommand{\attendant}{Attendant}

\newcommand{\shadowriders}{Shadow Riders}
\newcommand{\shadowrider}{Shadow Rider}

% RAIDERS

\newcommand{\blackcloaks}{Black Cloaks}
\newcommand{\blackcloak}{Black Cloak}


% DESTROYERS

\newcommand{\huntingchariot}{Hunting Chariot}

\newcommand{\repeaterbattery}{Repeater Battery}


% THE MENAGERIE

\newcommand{\kraken}{Kraken}

\newcommand{\hydra}{Hydra}

\newcommand{\mistleviathan}{Mist Leviathan}

%%%% Unit entries rules

%% CHARACTERS

% Dread Prince

\newcommand{\deadlyriposte}{}%
\newcommand{\deadlyripostedef}{%
	%
}%

%Beastmaster

\newcommand{\willbreakerscraft}{Willbreaker's Craft}
\newcommand{\willbreakerscraftdef}{%
	While within \distance{12} of one or more non-Fleeing models with \willbreakerscraft{}:
	\begin{itemize}
		\item Friendly non-Construct models with \toweringpresence{} gain \textbf{\minimised{} (Discipline Tests)}.
		\item Friendly models gain \textbf{\maximised{} (Stomp Attacks)}.
		\item Enemy models gain \textbf{\minimised{} (Stomp Attacks)}.
	\end{itemize}
}%

%Silexian Officer

\newcommand{\tactician}{Tactician}
\newcommand{\tacticiandef}{%
	Units count as being within \distance{8} of a non-Fleeing model with Academy Trained from another friendly unit if all of the following conditions are met:
	\begin{itemize}
		\item They consist entirely of Infantry models.
		\item More than half of their models have Academy Trained.
		\item They are joined by a model with Tactitian or they are within range of Commanding Presence of a non-Fleeing friendly model with Tactician.
	\end{itemize}
}


%Temple Exarch

\newcommand{\againstmeleeattacks}{against Melee Attacks}
\newcommand{\warsmith}{War Smith}
\newcommand{\warsmithdef}{%
	The model gains \textbf{\wizardadept{}}. In addition, the model part and \rnf{} model parts without Harnessed in its unit gain \textbf{\battlefocus{}} and \textbf{\frenzy{}}. \templemilitants{} additionally gain \textbf{\hatred{}} while a \warsmith{} is joined to their unit.%
}

\newcommand{\oracleofdoom}{Oracle of Doom}
\newcommand{\oracleofdoomdef}{%
	The model gains \textbf{\wizardadept{}}. In addition, the model part and \rnf{} model parts without Harnessed in its unit gain \textbf{\battlefocus{}} and \textbf{\frenzy{}}. \templemilitants{} additionally gain \textbf{\hatred{}} while an \oracleofdoom is joined to their unit.%
}

% Warlock Outcast

\newcommand{\irresistiblewill}{Irresistible Will}
\newcommand{\irresistiblewilldef}{%
	Dispelling rolls against spells cast by the model suffer a -2 Dispelling Modifier if the Casting Attempt was performed with 4 or more Magic Dice.
}

\newcommand{\mistrusted}{Mistrusted}
\newcommand{\mistrusteddef}{
	If the model is the General, Discipline Tests using its Commanding Presence suffer \minuss{}1 Discipline.
}

%% MOUNTS

% Manticore

\newcommand{\extraordinaryspecimen}{Extraordinary Specimen}%
\newcommand{\extraordinaryspecimendef}{%
	The \manticore{} gains \textbf{\stompattacks{\Dthree{}}} and \textbf{\toweringpresence{}}, and its base size is changed to 50\timess{}100 \si{\milli\meter}.%
}
\newcommand{\solitary}{Solitary}
\newcommand{\solitarydef}{%
	%
}
% Imperious Dragon

\newcommand{\meetingofmindsdef}{%
	The model gains \textbf{\scentofblood{}} and treats all friendly \beast{} models as \insignificant{}.%
}

%% CORE

% Corsairs

\newcommand{\viciousslavers}{Vicious Slavers}%
\newcommand{\viciousslaversdef}{%
	 Enemy models that are not immune to the effects of \fear{} in units in base contact with one or more models with \viciousslavers{} suffer -1 Discipline.
}

% Beast Breakers

\newcommand{\lashsting}{Lash's Sting}%
\newcommand{\lashstingdef}{%
	Units containing one or more models with \lashsting{} gain \textbf{\cannotbestomped{}}. At the start of each friendly Player Turn, for each unit that contains one or more models with \lashsting{}, choose another friendly unit within \distance{8} of that unit. Mounted models in a unit chosen once or more gain +\distance{1} Advance Rate until the end of the Movement Phase.%
}

%% SPECIAL

%Raptor Chariot
\newcommand{\thecrewmustchoose}{The Crew \textbf{must} choose}

% Obsidian Guard

\newcommand{\willofthesenate}{Will of the Senate}%
\newcommand{\willofthesenatedef}{%

	%
}%

\newcommand{\rakingclaws}{Raking Claws}
\newcommand{\rakingclawsdef}{
	Sweeping Attack. The enemy unit suffers 1 hit for each model with \rakingclaws{} in the unit. These hits are resolved with the Strength and Armour Penetration of model part with \rakingclaws{}.
}

% Gorgons

\newcommand{\petrifyingstare}{Petrifying Stare}
\newcommand{\petrifyingstaredef}{%
	At Initiative Step 10, each enemy unit in base contact with the model suffers 2 hits with \ArmourPenetration{} 10 and \magicalattacks{} that wound on\spacebeforecolon{}:%
			\begin{smallitemize}%
				\item 4+ for models of \heightstandard{} Height%
				\item 5+ for models of \heightlarge{} Height%
				\item 6+ for models of \heightgigantic{} Height%
			\end{smallitemize}%
}

% Divine Altar

\newcommand{\crucibleofslaughter}{Crucible of Slaughter}%
\newcommand{\crucibleofslaughterdef}{%
	The model gains \textbf{\attached{}}, \textbf{\exclusive{} (\rnf{} Infantry)}, \textbf{\frenzy{}}, \textbf{\notaleader{}}, and \textbf{\warplatform{}},  and it loses \channel{} (3). In addition, the following elements gain the corresponding rules while in units within \distance{12} of a friendly \crucibleofslaughter{}:
	\begin{itemize}
		\item \rnf{} model parts without \harnessed{} gain \textbf{\battlefocus{}} and \textbf{\frenzy{}}
		\item Temple Militants gain \textbf{\hatred{}}
	\end{itemize}%
}%


\newcommand{\effigyofdread}{Effigy of Dread}%
\newcommand{\effigyofdreaddef}{%
	The model gains \textbf{\fear{}}, \textbf{\fearless{}}, and  \textbf{\unbreakable{}}. Its Health Points are \textbf{set} to 6 and   and its \AdvanceRate{} and \MarchRate{} are \textbf{always} set to \distance{0}. The model cannot declare any Charges nor perform any Advance Moves, March Moves, Magical Moves, Pursuit Moves, nor Random Movement.
	In addition, friendly units within \distance{24} of the model gain \textbf{\fear{}}. Enemy units within \distance{24} of the model cannot benefit from \rallyaroundtheflag{} for \fear{} Tests.\newline
	%
}%

% Hunting Chariot

\newcommand{\destroyerrestriction}{
	For each \huntingchariot{} in the army, the maximum number is reduced by 1
}

\newcommand{\harpoonlauncher}{Harpoon Launcher}
\newcommand{\harpoonlauncherdef}{
	Units that suffer one or more  hits from this weapon lose \swiftstride{} (and cannot gain it in any way) until the start of the next friendly Player Turn.
}

% Repeater Battery

\newcommand{\daebboltthrower}{Daeb Bolt Thrower}%
\newcommand{\daebboltthrowerdef}{Note that the model can move and shoot.}%

%% THE MENAGERIE

% Kraken

\newcommand{\colossalkraken}{Colossal Kraken}%
\newcommand{\colossalkrakendef}{%
	The model gains +2 \HealthPoints{}, 2 additional \lashmaster{}s, and its base size is changed to 100\timess{}150 \si{\milli\meter}.%
}%
\newcommand{\colossalkrakencondition}{Armies with one or more \beastmaster{}s only}%

% Hydra

\newcommand{\ragedef}{%
	Whenever the model loses a Health Point, it gains +1 Attack Value. Whenever it gains a Health Point, it suffers \minuss{}1 Attack Value.%
}

\newcommand{\cutoneoff}{Cut one off\dots{}}%
\newcommand{\cutoneoffdef}{%
	For each successful \fortitude{} Save roll of a natural \result{6}, the model disregards another simultaneously suffered wound. If there aren't enough simultaneously suffered wounds to disregard, the model immediately Recovers 1 Health Point instead.%
}

% Mist Leviathan

\newcommand{\underthecoverofmists}{Under the Cover of Mists}%
\newcommand{\underthecoverofmistsdef}{%
	Enemy units within \distance{8} of one or more \mistleviathan{}s suffer \minuss{}1 to hit for Shooting Attacks. In addition, during the first Game Turn, friendly Infantry units gain \textbf{\hardtarget{}~(1)} while within \distance{8} of one or more \mistleviathan{}s.%
}
