
% Special Equipment Names

\newcommand{\cripplingfrost}{Crippling Frost}
\newcommand{\transcendence}{Transcendence}
\newcommand{\laceratingtouch}{Lacerating Touch}
\newcommand{\masteryofslaughter}{Mastery of Slaughter}
\newcommand{\prideofgardaecos}{Pride of Gar Daecos}

\newcommand{\sealoftherepublic}{Seal of the Republic}

\newcommand{\moithirmirror}{Moithir's Mirror}
\newcommand{\maskofthewarcrow}{Mask of the War Crow}
\newcommand{\sealoftheninthfleet}{Seal of the \nth{9} Fleet}
\newcommand{\beastmasterwhistle}{Beastmaster's Whistle}
\newcommand{\ceinranscales}{Ceinran's Scales}
\newcommand{\ringoftheobsidianthrones}{Ring of the Obsidian Thrones}

\newcommand{\executionericon}{Executioner's Icon}
\newcommand{\eyeofthegorgon}{Eye of the Gorgon}
\newcommand{\caedhrenpennon}{Caedhren's Pennon}

% Special Equipment Texts

\newcommand{\cripplingfrostdef}{%
	Enemy units in base contact with the bearer's model suffer \minuss{}2 Defensive Skill.%
}
\newcommand{\transcendencedef}{%
	For each unsaved wound inflicted on enemy models with this weapon, the wielder gains +1 \Strength{} and +1 \ArmourPenetration{} for the rest of the game, up to a maximum of +2 each.\columnbreak%You may place this \columnbreak were needed in your language
}
\newcommand{\laceratingtouchdef}{%
	Attacks made with this weapon gain +2 \ArmourPenetration{}. While using this weapon, the wielder gains +2 \AttackValue{} and \textbf{\fear{}}.%
}
\newcommand{\masteryofslaughterdef}{%
	Attacks made with this weapon gain \textbf{\artistryofdeath{}}, \textbf{\battlefocus{}}, \textbf{\lethalstrike{}}, and \textbf{\multiplewounds{2}{}}.%
}
\newcommand{\prideofgardaecosdef}{%
	While using this weapon, the wielder gains +1 \AttackValue{}, and attacks made with this weapon become \textbf{\divineattacks{}}.%
}


\newcommand{\sealoftherepublicdef}{%
	For each unsaved wound inflicted on enemy models with the wearer's Close Combat Attacks, the wearer gains +1 \Armour{} for the rest of the game.%
}


\newcommand{\executionericondef}{%
	The bearer and \rnf{} model parts with \ruthlessefficiency{} in the bearer's unit gain \textbf{\artistryofdeath{}}.%
}
\newcommand{\eyeofthegorgonrestriction}{Cannot be taken by units that count toward Core}
\newcommand{\eyeofthegorgondef}{%
	The bearer gains \textbf{\petrifyingstare{}} (see \hyperlink{DE4gorgons}{\gorgons{}} unit). Enemy units in base contact with the bearer \textbf{must} reroll successful \Discipline{} Tests.%
}
\newcommand{\caedhrenpennondef}{%
	Infantry models in the bearer's unit gain \textbf{\scentofblood{}} and \textbf{\swiftstride{}}.%
}


\newcommand{\moithirmirrordef}{%
	The bearer gains \textbf{\aegis{} (5,+ against Melee Attacks)}.
	In addition, at Initiative Step 0 of a Round of Combat in which one or more Melee Attacks are allocated towards or distributed onto the bearer's model (including Initiative Step 0), the bearer inflicts 3 hits with Strength 4, Armour Penetration 2, and \magicalattacks{} on each of the attacking models' units. This is considered a Special Attack.
}
\newcommand{\maskofthewarcrowdef}{%
	The bearer's unit gains \textbf{\fear{}}. In addition, the bearer and any friendly unit that contains one or more models with \fear{} within \distance{6} of the bearer's unit \textbf{must} reroll natural to-wound rolls of \result{1} with its Close Combat Attacks.%
}
\newcommand{\sealoftheninthfleetrestriction}{\silexianofficer{}s only}
\newcommand{\sealoftheninthfleetdef}{%
	If the bearer's unit consists entirely of Infantry models, it gains \textbf{\academytrained{}}.%
}
\newcommand{\beastmasterwhistlerestriction}{\beastmaster{}s only}
\newcommand{\beastmasterwhistledef}{%
	One use only. May be activated at the start of any friendly Charge Phase. Friendly \manticore{}s and friendly models with Type \beast{} within \distance{12} of the bearer gain \textbf{\maximised{} (Charge Range)} until the end of the Charge Phase.
}
\newcommand{\ceinranscalesdef}{%
	The bearer can cast \spellformat{\evocationspellfour}{\evocation} as a Bound Spell with Power Level (4/8).%
}
\newcommand{\ringoftheobsidianthronesrestriction}{Cannot be taken by \warlockoutcast{}s}
\newcommand{\ringoftheobsidianthronesdef}{%
	While within \distance{6} of the bearer, friendly units gain \textbf{Minimised (Break Tests, Panic Tests)}.%%
}
