
\part*{Narrative Scenarios}
\label{narrative_scenarios}

These scenarios contain more complex ideas and rules than the Gaming Scenarios. They can require unique Terrain Features or one or more specific armies to participate. They can also include uneven Army Points, with one side having a significantly larger force than the other.

Therefore these scenarios are not intended for balanced competitive play but for more entertaining games that tell a story.

Each Narrative Scenario contains detailed explanations on how it should be used as indicated in the following headings:

\startgamingscenarioheadings%
\gamingscenarioheading{Deployment} The Deployment Type used in the scenario. This can be one of the standard Deployment Types but it can also be unique. If so, everything needed to carry out the Deployment will be specified.

\gamingscenarioheading{Pre-Game Set-up} Which steps to perform before the battle begins, such as placing tokens for the objectives, or any restrictions pertaining to Army Lists.

\gamingscenarioheading{Scenario Special Rules} Any unique rules that affect the armies or the Battlefield in this scenario.

\gamingscenarioheading{Winning the Scenario} How to win the game. Most Narrative Scenarios have an original way of determining the winner, different from counting Battle Points.
\closegamingscenarioheadings%

\startnarrativescenariolist
\textbf{Number}&
\textbf{Scenario}&
\textbf{Page}\\
1 & \hyperref[TheGatesofGreed]{The Gates of Greed} & \pageref{TheGatesofGreed} \\
2 & \hyperref[TheTreasureoftheDragon]{The Treasure of the Dragon} & \pageref{TheTreasureoftheDragon} \\
3 & \hyperref[GreatPortalsoftheBarrenMountains]{Great Portals of the Barren Mountains} & \pageref{GreatPortalsoftheBarrenMountains} \\
4 &\hyperref[DivineIntervention]{Divine Intervention} & \pageref{DivineIntervention} \\
5 & \hyperref[AnEyeintheFuture]{An Eye in the Future} & \pageref{AnEyeintheFuture} \\
6 & \hyperref[MissionImpossible]{Mission Impossible} & \pageref{MissionImpossible} \\
7 & \hyperref[MarchtoVictory]{March to Victory} & \pageref{MarchtoVictory} \\
8 & \hyperref[StrategicObjections]{Strategic Objections} & \pageref{StrategicObjections} \\
9 & \hyperref[AProperBattle]{A Proper Battle} & \pageref{AProperBattle} \\
10 & \hyperref[WeathertheStorm]{Weather the Storm} & \pageref{WeathertheStorm} \\
11 & \hyperref[RunawayTrain]{Runaway Train} & \pageref{RunawayTrain} \\
12 & \hyperref[IntheMountains]{In the Mountains} & \pageref{IntheMountains} \\
\closenarrativescenariolist
