
\newnarrativescenario{5}{An Eye on the Future}
\label{AnEyeintheFuture}

\flufffont{Few are the ones able to foresee the future, and fewer still the ones able to do so and keep their sanity. The Oracle's prediction can help you reach glory\ldots{} or madness.}

\subsection*{Deployment}

Any of the standard Deployment Types.

\subsection*{Pre-Game Set-up}

You need a model to represent the Oracle. It can typically be a Wizard, a monster, or even a tower which the Oracle is supposed to be in. During the game, that model is treated as Impassable Terrain. Place at in the centre of the board.

\subsection*{Scenario Special Rules}

\subsubsection*{The Great Oracle}

At the end of your Movement Phase, you may ask the Oracle for predictions for each friendly Character that is not Fleeing 	and not Engaged in Combat within \distance{3} of the Oracle. For each Character, roll a D6 and place it next to the Character, referred to as a Fate Dice. When performing one of the following actions, you may replace any single rolled D6 with the Fate Dice (this is not considered rerolling the dice).

\begin{itemize}
\item Casting Attempts made by the Character
\item To-hit rolls for attacks made by the Character
\item To-wound rolls for attacks made by the Character
\item Armour Save rolls made the Character
\item Special Save rolls made by the Character
\item Charge Range rolls for the Character or its unit
\end{itemize}

As long as a Character has a Fate Dice, it suffers a negative modifier to its Discipline equal to half the value of the Fate Dice, rounding fractions up. No Character can have more than a single Fate Dice.

\subsection*{Winning the Scenario}

The players fight to gain the loyalty of the Oracle. Each time a Character or a unit is removed as a casualty within \distance{18} of the Oracle, and each time a unit Breaks within \distance{18} of the Oracle, the opponent of its owner gains 1 Victory Counter. Each unit can only award a single Victory Token per phase.

At the end of the game, the player with the most Victory Counters wins the game.
