\part*{Gaming Scenarios}
\label{gaming_scenarios}

These scenarios are intended to be used for everyday gaming, and can be played using any armies and normal Terrain, replacing the normal Deployment Types and Secondary Objectives in the Rulebook.

Each Gaming Scenario consists of the following elements:

\startgamingscenarioheadings%
\gamingscenarioheading{Deployment} The Deployment Type used in the scenario. This can be one of the standard Deployment Types but it can also be unique. If so, everything needed to carry out the Deployment will be specified.

\gamingscenarioheading{Pre-Game Set-up} Which steps to perform place before the battle begins, such as placing tokens for the Secondary Objective. 

\gamingscenarioheading{Scenario Special Rules} Any unique rules that affect the armies or the Battlefield in this scenario.

\gamingscenarioheading{Winning the Secondary Objective} How to win the Secondary Objective. If there is a winner of the Secondary Objective, that player gains 3 additional Battle Points while the loser of the Secondary Objective loses 3 Battle Points, as usual.
\closegamingscenarioheadings%

\subsection*{Scenario Chart}

You can use the following chart to randomly determine which scenario to play. Roll a D3 to choose the scenario bracket (see the table below), and then roll a D6 to determine the exact scenario to be played.

\startgamingscenariolist
\textbf{D3 Result}&
\textbf{D6 Result}&
\textbf{Scenario}&
\textbf{Page}\\
1&
1&
\hyperref[Misdirections]{Misdirections}&
\pageref{Misdirections}\\
1&
2&
\hyperref[HiddenTreasures]{Hidden Treasures}&
\pageref{HiddenTreasures}\\
1&
3&
\hyperref[DarkVisions]{Dark Visions}&
\pageref{DarkVisions}\\
1&
4&
\hyperref[LostRuins]{Lost Ruins}&
\pageref{LostRuins}\\
1&
5&
\hyperref[AncientArtefact]{Ancient Artefact}&
\pageref{AncientArtefact}\\
1&
6&
\hyperref[TheAdversarysTask]{The Adversary's Task}&
\pageref{TheAdversarysTask}\\
\hline
2&
1&
\hyperref[TheLongMarchHome]{The Long March Home}&
\pageref{TheLongMarchHome}\\
2&
2&
\hyperref[MeteorShower]{Meteor Shower}&
\pageref{MeteorShower}\\
2&
3&
\hyperref[TheHolyGrail]{The Holy Grail}&
\pageref{TheHolyGrail}\\
2&
4&
\hyperref[TheHiddenKings]{The Hidden Kings}&
\pageref{TheHiddenKings}\\
2&
5&
\hyperref[TheHiddenKings]{Despoilers}&
\pageref{TheHiddenKings}\\
2&
6&
\hyperref[DominatingTheField]{Dominating the Field}&
\pageref{DominatingTheField}\\
\hline
3&
1&
\hyperref[BarrelOfStout]{Barrel of Stout}&
\pageref{BarrelOfStout}\\
3&
2&
\hyperref[EscapeFromBeyondTheVeil]{Escape from Beyond the Veil}&
\pageref{EscapeFromBeyondTheVeil}\\
3&
3&
\hyperref[Carnage]{Carnage}&
\pageref{Carnage}\\
3&
4&
\hyperref[HoldTheLine]{Hold the Line}&
\pageref{HoldTheLine}\\
3&
5&
\hyperref[FoulManners]{Foul Manners}&
\pageref{FoulManners}\\
3&
6&
\hyperref[MultipleObjectives]{Multiple Objectives}&
\pageref{MultipleObjectives}\\
\closegamingscenariolist
