
% Army Model Rules Names

\newcommand{\packtactics}{Pack Tactics}
\newcommand{\drunkard}{Drunkard}
\newcommand{\sober}{Sober}
\newcommand{\drunk}{Drunk}
\newcommand{\lootedbooze}{Looted Booze}
\newcommand{\huntingcall}{Hunting Call}

\newcommand{\primalinstinct}{Primal Instinct}

\newcommand{\beastaxe}{Beast Axe}


% Army Model Rules Texts

\newcommand{\packtacticsdef}{%
	Units consisting entirely of models with Pack Tactics gain \textbf{\devastatingcharge{\swiftstride}} while they are Located in the Charged unit's Flank or Rear Arc.%
}
\newcommand{\drunkarddef}{%
	The unit may gain one of two different sets of effects depending on whether it shows up \sober{} or \drunk{} on the Battlefield. At step 8 of the Pre-Game Sequence (after Spell Selection), the player \textbf{must} choose whether a \drunkard{} unit is \sober{} or \drunk{}. \drunk{} Characters cannot join units containing any \sober{} models and vice versa (models without \drunkard{} are considered neither \drunk{} nor \sober{}).%
}
\newcommand{\soberdef}{%
	The model gains \textbf{\lighttroops} and \textbf{\vanguard}. A unit that has been \sober{} once loses \scoring{} for the rest of the game. If playing Capture the Flags, \scoring{} is not lost.%
}
\newcommand{\drunkdef}{%
	The model gains \textbf{\devastatingcharge{+1 \St{}, +1 \AP{}}} and \textbf{\fearless}. \drunk{} units cannot Ambush.%
}
\newcommand{\lootedboozedef}{%
	One use only. May be activated at the start of any Player Turn. All models with \drunkard{} in the model's unit change from \sober{} to \drunk{}.%
}
\newcommand{\huntingcalldef}{%
	If the army includes a model with Hunting Call, the owner may:
	\begin{itemize}%
		\item Choose to roll for \ambush{} for units with one or more models with \packtactics{} starting from the owner's Player Turn 1 (but still at the end of step 2 of the Movement Phase Sequence), unless the owner has the first Player Turn.
		\item Reroll \ambush{} rolls of 1--2 for units with one or more models with \packtactics{}.
		\end{itemize}%
	Hunting Call is in effect even if the model is Ambushing and has not arrived on the Battlefield yet.%
}

\newcommand{\primalinstinctdef}{%
	At the start of each Round of Combat that the model's unit is fighting, each unit with one or more model parts with this Attack Attribute \textbf{must} take a Discipline Test. If the test is passed, all model parts with \primalinstinct{} in the unit \textbf{must} reroll failed to-hit rolls during this Round of Combat.%
}

\newcommand{\beastaxedef}{%
	Attacks made with this weapon gain +1 Strength, +1 Armour Penetration, and always strike at Initiative Step 0. The wielder gains +2 Defensive Skill unless wielding another weapon.\newline
This weapon cannot be enchanted with Weapon Enchantments from the list of Common Special Items.%
}
