% Honours
%%%

\newcommand{\honour}{Honour}
\newcommand{\honours}{Honours}
\newcommand{\honoursInitial}{Ho}

\newcommand{\honoursmountoptions}{The Character's Mount Options are replaced with}


\newcommand{\honoursforhighprincesandcommanders}{Honours for High Princes and Commanders}

\newcommand{\masterofcanreigtower}{Master of Canreig Tower}
\newcommand{\masterofcanreigtowerdef}{%
	The model gains \textbf{\masterofspellcrafting}, \textbf{\proteanmagic}, and \textbf{\wizardadept}. The model has access to \alchemy{}, \cosmology{}, \druidism{}, \shamanism{}, and \witchcraft{}.
}
\newcommand{\highprincemustgainlearnedspells}{\highprince{} \textbf{must} gain\newline\suboptionindent{} 3 additional Learned Spells}
\newcommand{\masterofcanreigtowerrestriction}{Models on foot only}

\newcommand{\queenscavalier}{Queen's Cavalier}
\newcommand{\queenscavalierdef}{%
	The model part gains \textbf{\devastatingcharge{} (+1 \At{}, \fear)}.\newline{}
	If the army contains one or more \heightlarge{} or \heightgigantic{} models with \queenscavalier{}:
\begin{itemize}
	\item The maximum sum of \ancientallies{} values in the army is increased by 2.
	\item Characters is increased to \enquote{Max. \SI{50}{\percent}}.
	\item All Characters in the army \textbf{must} be Large Cavalry or Gigantic Beasts.
	\item Dragons and Ancient Dragons become \zerotoXmountsperarmy{2}.
	\item Sea Guard Reapers and Sky Sloops may not be taken in the army.
\end{itemize}%
}
\newcommand{\queenscavalierrestriction}{Models on foot or on Elven Horse, Dragon, or Ancient Dragon only}%

\newcommand{\fleetofficer}{Fleet Officer}
\newcommand{\fleetofficerdef}{%
	The model part gains \textbf{\steadyaim} and, when using a \skyreaper{}, +2 to-hit. An army with one or more Fleet Officers may add +1 to the roll for choosing Deployment Zones. While within the model's range of \commandingpresence{} or \rallyaroundtheflag{} (if applicable), models with Martial Discipline gain \textbf{Minimised (Panic Tests)}.\columnbreak%
}
\newcommand{\fleetofficerrestriction}{Models on foot or on Giant Eagle, Griffon, or Sky Sloop only}%

\newcommand{\highwardenoftheflame}{High Warden of the Flame}
\newcommand{\highwardenoftheflamerestriction}{Models on foot only}
\newcommand{\highwardenoftheflamedef}{%
	The model gains \textbf{\aegis{} (4+)}, \textbf{\fearless}, \textbf{\flamingattacks}, \textbf{\magicresistance{} (1)}, and cannot be equipped with a \shield{}.\columnbreak%
}
\newcommand{\highwardenoftheflanerestriction}{Models on foot only}

\newcommand{\queenscompanion}{Queen's Companion}
\newcommand{\queenscompaniondef}{%
	When shooting with a \longbow{} without Weapon Enchantment, the model's weapon gains \shots{3}. In addition, the model's unit gains \quicktofire{}.\newline
	One choice only:%
}
%\newcommand{\queenscompanionoption}{%
%	\faemiasma{}, \scout{}, \exclusive{} (\greywatchers{})%
%}
\newcommand{\queenscompanionrestriction}{0--2 Honours per Army. Models on foot only}%

\newcommand{\royalhuntsman}{Royal Huntsman}
\newcommand{\royalhuntsmandef}{%
	The model gains \textbf{\lionsfur} and the model's unit gains \textbf{\valiant}. When using a \gw{}, the model part gains \textbf{\multiplewounds{}{} (2, against Large and Beast, Large and Cavalry, Gigantic)}.%
}
\newcommand{\royalhuntsmanrestriction}{Models on foot or on Lion Chariot only}%



\newcommand{\honoursformages}{Honours for Mages}

\newcommand{\asfadscholar}{Asfad Scholar}
\newcommand{\asfadscholardef}{%
	The range of the Wizard's non-Bound Spells is increased by \distance{6}. Aura spells gain +\distance{3} range instead. Spells with type Caster are unaffected. The Wizard can cast \textbf{\spellformat{Drain Magic}{}} as a Bound Spell with Power Level (4/8).\DTLpar%
	\textbf{Drain Magic}: \range{18}, Type \universal{}, Duration \instant{}.\newline%
	All spells with duration \oneturn{} for which the target of Drain Magic or a model or model part inside that unit was the spells' target immediately come to an end (note that if any of these spells had more than one target, their effects also end for these targets).\columnbreak%
}
\newcommand{\maybemountedasnormal}{May be mounted as normal}
\newcommand{\asfadscholarrestriction}{Wizard Masters only}%

\newcommand{\orderofthefieryheart}{Order of the Fiery Heart}
\newcommand{\orderofthefieryheartdef}{%
	The model gains \textbf{\flamingattacks}. The model replaces its available Paths with Alchemy and Pyromancy, and ignores the \missile{} and \damage{} spell types for \spellformat{\alchemyspellfour}{\alchemy} and all \pyromancy{} spells, but only when targeting units that are Engaged in Combat with the model.\DTLpar%
	The first time in each Magic Phase that the model successfully casts a Learned Spell, its mount (if there is any) gains +\distance{1} Advance Rate, +\distance{2} March Rate, and +2 Attack Value. The effects last until the start of the next friendly Magic Phase. In addition, the model gains access to the following options:%
%	\orderofthefieryheartlogos{}%
}
\newcommand{\ifmounted}{pts / if mounted}
\newcommand{\orderofthefieryheartrestriction}{Models on foot or on Dragon only}