
% Special Equipment Names

\newcommand{\novaflare}{Nova Flare}
\newcommand{\sliveroftheblazingdawn}{Sliver of the Blazing Dawn}
\newcommand{\elusheartwood}{Elu's Heartwood}

\newcommand{\gleamingrobe}{Gleaming Robe}
\newcommand{\protectionofdorac}{Protection of Dorac}
\newcommand{\starmetalalloy}{Star Metal Alloy}
\newcommand{\daemonsbane}{Daemon's Bane}

\newcommand{\navigatorsbanner}{Navigator's Banner}
\newcommand{\bannerofbecalming}{Banner of Becalming}
\newcommand{\warbannerofryma}{War Banner of Ryma}

\newcommand{\bookofmeladys}{Book of Meladys}
\newcommand{\ringofthepearlthrone}{Ring of the Pearl Throne}
\newcommand{\diademofprotection}{Diadem of Protection}
\newcommand{\amethystcrystal}{Amethyst Crystal}
\newcommand{\glitteringlacquer}{Glittering Lacquer}

% Special Equipment Texts

\newcommand{\novaflaredef}{%
	Attacks made with this weapon gain \textbf{\devastatingcharge{} (+1 \At{})}, \textbf{\lethalstrike}, and become \textbf{\divineattacks}.\newline%
	One use only. May be activated at the start of any Round of Combat. The wielder counts as Charging for the purpose of \devastatingcharge{}.%
}
\newcommand{\sliveroftheblazingdawndef}{%
	Attacks made with this weapon gain +1 Strength and +2 Armour Penetration. Each successful to-hit roll with this weapon causes two hits instead of one.%
}
\newcommand{\elusheartwooddef}{%
	This weapon gains \shots{3}, \St{} as user +1, and \AP{} as user +1.%
}

\newcommand{\gleamingroberestriction}{Standard Height Mages only}
\newcommand{\gleamingrobedef}{%
	The wearer gains \textbf{\aegis{} (3+)}. In addition, its Armour is \textbf{set} to 1 and can \textbf{never} be improved beyond this. If the wearer Miscasts and rolls Magical Inferno or Witchfire, the number of hits is halved, rounding fractions up.%
}
\newcommand{\protectionofdoracdef}{%
	The wearer gains +2 Armour and +2 Defensive Skill.%
}
\newcommand{\starmetalalloydef}{%
	The first time the bearer's model suffers an unsaved wound from an attack with \multiplewounds{X}{} while using this Shield, the number of wounds suffered is halved, rounding fractions up.%
}
\newcommand{\daemonsbanedef}{%
	The wearer gains +2 Armour against \magicalattacks{}.%
}

\newcommand{\navigatorsbannerdef}{%
	\rnf{} models in the bearer's unit gain \textbf{\distracting} in the First Round of Combat against attacks from enemies Engaged in the bearer's unit's Front Facing.%
}
\newcommand{\bannerofbecalmingrestriction}{Cannot be taken by units that count towards Core}
\newcommand{\bannerofbecalmingdef}{%
	In the opponent's Magic Phase, during Siphon the Veil before converting Veil Tokens into Magic Dice, remove one Veil Token from the opponent's Veil Token pool and add one Veil Token to your Veil Token pool.%
}
\newcommand{\warbannerofrymadef}{%
	\rnf{} model parts without \harnessed{} in a unit with one or more War Banners of Ryma gain \textbf{\devastatingcharge{} (+1 \St{})}. In addition, all Infantry models in the unit gain \textbf{\devastatingcharge{} (+\distance{1} \Ad{})}.%
}

\newcommand{\bookofmeladysdef}{%
	Once per Magic Phase, the bearer may reroll a single Magic Dice when making a casting roll, provided the spell was not Miscast. When rerolling a natural \result{1}, the rerolled Magic Dice benefits from Fizzle (if the Casting Attempt fails) regardless of the value rolled from the reroll.%
}
\newcommand{\ringofthepearlthronerestriction}{Cannot be taken by models with Towering Presence}
\newcommand{\ringofthepearlthronedef}{%
	Weapon Enchantments in the bearer’s unit and in units that are in base contact with the bearer are ignored.%
}
\newcommand{\diademofprotectiondef}{%
	The bearer gains \textbf{\aegis{} (+2, max 4+)}.%
}
\newcommand{\amethystcrystaldef}{%
	Dispelling rolls made by the bearer's army gain a +1 modifier.%
}
\newcommand{\glitteringlacquerrestriction}{Cavalry models only}
\newcommand{\glitteringlacquerdef}{%
	The bearer gains \textbf{\hardtarget{} (1)}.%
}
