% Army Model Rule Names

\newcommand{\martialdiscipline}{Martial Discipline}
\newcommand{\masterofspellcrafting}{Master of Spellcrafting}
\newcommand{\valiant}{Valiant}
\newcommand{\ancientallies}{Ancient Allies}

\newcommand{\faemiasma}{Fae Miasma}
\newcommand{\moonlightarrows}{Moonlight Arrows}

\newcommand{\dragonforgedarmour}{Dragonforged Armour}
\newcommand{\lionsfur}{Lion's Fur}

% Army Model Rule Texts

\newcommand{\martialdisciplinedef}{%
Units with more than half of their models with Martial Discipline gain \textbf{\minimised{Discipline Tests}}. This instance of \minimised{} cannot be used for Panic Tests and Break Tests.%
}

\newcommand{\masterofspellcraftingdef}{%
The Wizard's spells have their Casting Value reduced by 1.%
}

\newcommand{\valiantdef}{%
The model is immune to the effects of \fear{}. If more than half of a unit's models have \valiant{}, the unit automatically passes Panic Tests caused by \terror{}.%
}

\newcommand{\ancientalliesdef}{
	The sum of the \ancientallies{} values stated in brackets of all models in the army is restricted to 1 per 1500 Army Points, rounding fractions up.
}

\newcommand{\meetingofmindsdef}{
	The \dragon{} model part gains \textbf{\channel{1}}.
}

\newcommand{\faemiasmadef}{%
This Attack Attribute can only be used with Longbows and Paired Weapons.\newline%
When a unit is hit by attacks with \faemiasma{}, it \textbf{must} take a Resilience Test for each hit, using the Resilience that the largest proportion of models in the unit has. Use the higher value in case of a tie. If one or more Resilience Tests are failed, all models in the unit are affected by \faemiasma{} until the start of the Active Player's next Player Turn. A model that is affected by one or more instances of \faemiasma{} suffers a \minuss{}1 to-hit modifier (both for Shooting Attacks and Close Combat Attacks).%
}

\newcommand{\moonlightarrowsdef}{%
This Attack Attribute can only be used with Bows or Longbows without Weapon Enchantments. The attacks become \textbf{\flamingattacks} and \textbf{\magicalattacks}, and they gain Strength 4 and Armour Penetration 1.%
}

\newcommand{\dragonforgedarmourdef}{%
\ha{}. The wearer gains \textbf{\aegis{} (3+, against \flamingattacks{})} and \textbf{\aegis{} (6+)}, and automatically fails all \fortitude{} Saves.%
}

\newcommand{\lionsfurdef}{%
If on foot, the wearer gains +1 Armour, which is improved to +2 Armour against Shooting Attacks.%
}
