
% Front side

\newcommand{\weatherspell}{Weather Spell}

\newcommand{\stormtitlea}{Mud Slicks}
\newcommand{\stormsubtitlea}{Sinkhole}
\newcommand{\stormnotea}{%
	Charging units do not benefit from Charging Momentum and instead suffer \minuss{}1 Agility.%
}

\newcommand{\stormtitleb}{Pouring Rain}
\newcommand{\stormsubtitleb}{Flash Flood}
\newcommand{\stormnoteb}{%
	Shooting Attacks suffer \minuss{}1 to hit. In addition, no model can draw Line of Sight to targets farther away than \distance{30}.%
}

\newcommand{\stormtitlec}{Howling Wind}
\newcommand{\stormsubtitlec}{Tornado}
\newcommand{\stormnotec}{%
	Shooting Attacks with Strength 5 or less suffer \minuss{}1 to hit.%
}

\newcommand{\stormtitled}{Thunderous Skies}
\newcommand{\stormsubtitled}{Call Lightning}
\newcommand{\stormnoted}{%
	Models making any Flying Movement (including Advance Moves, Reforms, etc.) take a Dangerous Terrain (2) Test at the end of the movement, which is not considered to be caused by Terrain.%
}

\newcommand{\stormtitlee}{Mist}
\newcommand{\stormsubtitlee}{Fog}
\newcommand{\stormnotee}{%
	No model can draw Line of Sight to targets farther away than \distance{18}.%
}

\newcommand{\stormtitlef}{Snap Freeze}
\newcommand{\stormsubtitlef}{Chilling Frost}
\newcommand{\stormnotef}{%
	Water Terrain becomes Dangerous Terrain (1) for all models, and is otherwise treated as Open Terrain. Models that treat Hills and Ruins as Dangerous Terrain add 1 to the value of any Dangerous Terrain Tests. All other models treat Hills and Ruins as Dangerous Terrain (1) instead. In addition, Charge Range rolls are subject to Minimised Roll.%
}

\newcommand{\stormtitleg}{Eclipse}
\newcommand{\stormsubtitleg}{Chosen One}
\newcommand{\stormnoteg}{%
	Successful Armour, Aegis and Fortitude Saves must be rerolled.%
}

\newcommand{\stormtitleh}{Calm and Clear}
\newcommand{\stormsubtitleh}{Eye of the Storm}
\newcommand{\stormnoteh}{%
	No additional effect.%
}

% Back side

\newcommand{\stormbacksubtitle}{SORCEROUS STORM}% back side bottom
