
% Front side

\newcommand{\dgsubtitle}{%
	The \sinversion{colored} text is additionally used if the Active Player chooses to yield to this sin.%
}
\newcommand{\dgsubmagicdice}{\sinversion{Active Player}}

\newcommand{\dgtitlea}{Yield to Pride}
\newcommand{\dgnotea}{\sinversion{%
	The Active Player must issue and accept Duels with a Character whenever possible (this cannot be prevented by issuing or accepting a Duel with a Champion first) and cannot voluntarily Flee or Stand and Shoot as Charge Reactions.%
}}

\newcommand{\dgtitleb}{Yield to Father Chaos}
\newcommand{\dgnoteb}{\sinversion{%
	The Active Player draws two additional Flux Cards; they can yield to neither, either, or both sins on these Flux Cards. By yielding to both sins they gain +4 Magic Dice, by yielding to one they gain +2 Magic Dice. The two additional Flux Cards are returned to the deck.%
}}

\newcommand{\dgtitlec}{Yield to Envy}
\newcommand{\dgnotec}{\sinversion{%
	The Active Player's units cannot use the General's Commanding Presence.%
}}

\newcommand{\dgtitled}{Yield to Greed}
\newcommand{\dgnoted}{\sinversion{%
	The Active Player's units gain Frenzy against enemy units that contain one or more Special Items.%
}}

\newcommand{\dgtitlee}{Yield to Sloth}
\newcommand{\dgnotee}{\sinversion{%
	The Active Player's units may not perform March Moves, and all of their Shooting Attacks gain Unwieldy.%
}}

\newcommand{\dgtitlef}{Yield to Lust}
\newcommand{\dgnotef}{\sinversion{%
	All enemy units gain Distracting and Hard Target.%
}}

\newcommand{\dgtitleg}{Yield to Wrath}
\newcommand{\dgnoteg}{\sinversion{%
	The Active Player's units gain Fearless and suffer \minuss{}2 Defensive Skill.%
}}

\newcommand{\dgtitleh}{Yield to Gluttony}
\newcommand{\dgnoteh}{\sinversion{%
	The Active Player's units automatically pass all Restrain Pursuit Tests and may not Pursue or Overrun.%
}}

% Back side

\newcommand{\darkgodsbacksubtitle}{DARK GODS}% back side bottom