
\newcommand{\sorcerousstormspells}{Sorcerous Storm Spells}

\newcommand{\ssintro}{%
	The Sorcerous Storm Flux Cards contains Weather Spells that may be cast by any of the Active Player's Wizards.\newline%
	 The spell number corresponds to the associated Flux Card number.%
}
\newcommand{\fluxcard}{Flux Card}

\newcommand{\ssspellone}{Sinkhole}
\newcommand{\ssspellonedef}{%
	The target suffers 2D6 hits with Strength 4 and Armour Penetration 0.%
}

\newcommand{\ssspelltwo}{Flash Flood}
\newcommand{\ssspelltwodef}{%
	Place a Water Terrain Feature underneath the target (this can be substituted by placing a marker or the spell card next to the unit). This Water Terrain always extends to the edges of the target's Unit Boundary (even if the unit moves or changes formation).%
}

\newcommand{\ssspellthree}{Tornado}
\newcommand{\ssspellthreedef}{%
	The target is Shaken.%
}

\newcommand{\ssspellfour}{Call Lightning}
\newcommand{\ssspellfourdef}{%
	Roll a D6. On a roll of 2+, the target suffers D6 Hits, plus an additional D3 hits if at least one model in the target has Fly. Hits are resolved with Strength 6 and Armour Penetration 10.\newline%
	On a roll of \result{1}, the Caster's unit is affected instead.%
}

\newcommand{\ssspellfive}{Fog}
\newcommand{\ssspellfivedef}{%
	No model in the target unit can draw Line of Sight to targets farther away than \distance{12}.%
}

\newcommand{\ssspellsix}{Chilling Frost}
\newcommand{\ssspellsixdef}{%
	The target suffers \minuss{}1 Strength, \minuss{}1 Armour Penetration, and \minuss{}2 Agility.%
}

\newcommand{\ssspellseven}{Chosen One}
\newcommand{\ssspellsevendef}{%
	This spell may only target Characters. The target gains +1 Discipline, Commanding Presence, and Rally Around the Flag.%
}

\newcommand{\ssspelleight}{Eye of the Storm}
\newcommand{\ssspelleightdef}{%
	Immediately after step 3 of the Magic Phase Sequence of the Active Player's next Magic Phase (Siphon the Veil), the target may automatically cast the Weather Spell for that turn's Flux Card, using no Magic Dice and achieving a total casting roll of 8 (it may be dispelled as normal). The spell then ends.%
}
